% Introduction to the EU: Midterm All-in-One (History, Institutions, Readings, Exam Tips)
% Text-to-speech friendly version (simple sections, no columns or margin notes)

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=2cm]{geometry}
\usepackage{enumitem}
\setlist{nosep,leftmargin=1.5em}
\raggedright

\begin{document}

\section*{Introduction to the EU Midterm All-in-One}

This sheet is built only from your course notes, readings, and slides in the repository.

\subsection*{How the exam works}
\begin{itemize}
\item The exam is not designed to be tricky or for “geniuses”, but you must have studied and have an overview.
\item Time: about two hours; enough to read, think, plan, and then write.
\item Task: read short texts carefully; identify the main idea, the argument, and one key expression; place the text in the long process of European integration.
\item Typical prompts: provide context for a statement; identify the debate, author, or moment; explain the specific meaning of key terms; compare or contrast texts.
\item What the professor wants: place the text in time and space; link it to the course blocks (history, institutions, policies, foreign policy); use course vocabulary.
\item Answer structure: name the concept or author; define it in one clear sentence; give two or three specific pieces of evidence; conclude by linking back to the question.
\end{itemize}

\subsection*{The exam as a ``movie''}
\begin{itemize}
\item Think of the course as a whole story and the exam text as one frame from that movie.
\item Your job is to know the whole story first: the main ``scenes'' are the treaties, the crises, the enlargements, and the institutional changes.
\item When you see an exam text, ask: which scene does this belong to? Which stage of integration? Which block does it touch?
\item You do not need to summarise everything in the text; you need to show that you understand how this one frame fits into the bigger picture.
\end{itemize}

\section*{1. Five stages of integration}
\begin{itemize}
\item Nineteen forty five to nineteen fifty eight: foundations after the Second World War. Marshall Plan, Council of Europe, NATO, and the European Coal and Steel Community.
\item Nineteen fifty eight to nineteen seventy three: from the Treaty of Rome to the first oil crisis. European Economic Community and Euratom, customs union, common market, Common Agricultural Policy, Luxembourg Compromise, and first enlargement in nineteen seventy three.
\item Nineteen seventy three to nineteen ninety two: crises and adaptation. Oil shock, stagflation, Southern enlargement, Single European Act, and path to Maastricht.
\item Nineteen ninety two to the present: from Maastricht to today. European Union, euro, pillars, Schengen, Lisbon, big enlargements, debates on migration, identity, and the Green Deal.
\item Two thousand eight crisis: global financial and euro crisis as a new phase inside this long period.
\end{itemize}

\section*{2. Four blocks of the course}
\begin{itemize}
\item Block one: history and origins: Schuman, Rome, ECSC and EEC, crises, Southern enlargement, Single European Act, Maastricht, enlargements.
\item Block two: institutions: executive, legislative, judiciary; twin executive, Parliament, Council, Court of Justice, European Central Bank, agencies.
\item Block three: policies: euro and Economic and Monetary Union, Common Agricultural Policy, citizenship, migration, Green Deal.
\item Block four: foreign and security policy: Common Foreign and Security Policy, NATO context, external dimension.
\end{itemize}

\section*{3. History milestones}
\begin{itemize}
\item Marshall Plan, OEEC, Council of Europe, NATO, and the European Coal and Steel Community in the late nineteen forties and early nineteen fifties.
\item European Defence Community: France blocked a supranational European army; economics was chosen instead as the path to integration.
\item Schuman Plan in nineteen fifty: common management of coal and steel under a High Authority; ``Europe Day'' is nine May.
\item Treaty of Paris in nineteen fifty one: creates the ECSC with six members (France, Germany, Italy, Belgium, Netherlands, Luxembourg).
\item Treaty of Rome in nineteen fifty seven: creates the EEC and Euratom and sets the path to a common market and customs union.
\item Empty chair crisis and Luxembourg Compromise: France withdrew; ``vital national interest'' veto; paralysis for about fifteen years.
\item Nineteen sixty seven: ECSC, EEC, Euratom merged into one European Community; customs union completed nineteen sixty eight.
\item Hague Summit nineteen sixty nine: enlargement and EMU on the agenda; the ``bandwagon'' rolled again.
\item First enlargement nineteen seventy three: UK, Ireland, Denmark; Norway voted no; UK had been vetoed twice by de Gaulle before.
\item Oil crisis nineteen seventy three: OPEC weapon; stagflation; no common EEC energy response.
\item Southern enlargement: Greece nineteen eighty one, Spain and Portugal nineteen eighty six.
\item Single European Act nineteen eighty six: single market and qualified majority voting extended.
\item Maastricht nineteen ninety two: EU, euro path, three pillars, citizenship; UK opt-outs.
\item Schengen: no internal borders; twenty-six countries, over four hundred million people.
\item Two thousand four: ``Big Bang'' of ten countries; Constitutional Treaty rejected (France, Netherlands).
\item Lisbon two thousand seven: Plan B; President of European Council; High Representative; more power to Parliament.
\item Nineteen ninety nine Commission crisis: fraud exposed; Parliament refused budget; Commission resigned.
\end{itemize}

\subsection*{Enlargements and Copenhagen criteria}
\begin{itemize}
\item Copenhagen criteria (political): democracy, rule of law, human rights, minority protection; (economic): functioning market economy, ability to cope with EU competition; (legal): adopt and implement the acquis communautaire.
\item Enlargements: nineteen seventy three (United Kingdom, Ireland, Denmark), nineteen eighty one (Greece), nineteen eighty six (Spain and Portugal), nineteen ninety five (Austria, Finland, Sweden), two thousand four (ten eastern states: e.g. Poland, Hungary, Czech Republic, Estonia, Latvia, Lithuania, Slovenia, Slovakia, Malta, Cyprus), two thousand seven (Bulgaria and Romania), two thousand thirteen (Croatia).
\item EEA and EFTA: Norway voted no twice (fishing, oil); is in the European Economic Area but not the EU; Iceland and Liechtenstein also in the EEA; Switzerland is in neither EU nor EEA but has bilateral agreements; EFTA was the UK's alternative (free trade without supranational transfer).
\end{itemize}

\section*{4. Institutions overview}
\begin{itemize}
\item Executive branch: European Council plus European Commission. The European Council sets political direction; the Commission proposes laws and implements them.
\item Legislative branch: European Parliament plus Council of the European Union. They are co-legislators.
\item Judiciary: Court of Justice of the European Union. It ensures the uniform interpretation and application of EU law and established the supremacy of EU law.
\item Other bodies: European Central Bank, Court of Auditors, and various agencies (e.g. EU Intellectual Property Office).
\item Lisbon added: permanent President of the European Council and High Representative for Foreign Affairs; ``twin executive'' can mean European Council plus Commission, but externally the question ``who speaks for the EU?'' remains; many voices, confusion in foreign policy.
\item Key institution roles:
  \begin{itemize}
  \item Commission: engine room; guardian of the treaties; initiates legislation; one commissioner per portfolio.
  \item Parliament: only directly elected EU institution; represents citizens; co-legislator.
  \item Council of the EU: ministers from member states; represents governments; adopts laws with Parliament.
  \item European Council: heads of state and government; defines the overall political direction; not a co-legislator.
  \end{itemize}
\end{itemize}

\section*{5. Policies: CAP, EMU, and Green Deal}
\begin{itemize}
\item Common Agricultural Policy: early and deep common policy on agriculture; common prices and subsidies; central to France; important for the budget and for understanding conflicts between member states; ``butter mountains'' and ``wine lakes''; still controversial.
\item Four freedoms: goods, services, capital, and people; the core of the single market.
\item Economic and Monetary Union and the euro: single currency, European Central Bank, debates on core and periphery, and crisis management, especially after two thousand eight.
\item Greek crisis and ECB: debt crisis, austerity, political and social cost; Draghi in two thousand twelve said the ECB would do ``whatever it takes'' to save the euro; calmed markets; democratic concerns because the ECB is not elected and can dictate to governments.
\item Green Deal and de-industrialisation: connection between climate policy, industrial policy, and the rise of populism, especially in cases like Germany.
\item Cohesion policy: structural funds, European Investment Bank, Committee of the Regions; redistribution to poorer regions; part of the story of Southern and Eastern enlargement.
\end{itemize}

\subsection*{Southern enlargement and Gibraltar}
\begin{itemize}
\item Greece nineteen eighty one: Colonels' dictatorship until nineteen seventy four; Cyprus conflict; joining the EC was democracy consolidation.
\item Portugal nineteen eighty six: Carnation Revolution nineteen seventy four; decolonisation; revolution not negotiated transition.
\item Spain nineteen eighty six: Franco died nineteen seventy five; negotiated transition; nineteen eighty two World Cup as soft power; France worried about CAP and farming; fishing, steel, textiles; cohesion for poorer regions.
\item Gibraltar: British since the Treaty of Utrecht; Franco closed the border in nineteen sixty nine to pressure the UK; families split for thirteen years; border partially reopened nineteen eighty two (Felipe González); part of Spain's accession talks in nineteen eighty six.
\end{itemize}

\subsection*{Delors and the revival}
\begin{itemize}
\item Jacques Delors: Commission President nineteen eighty five to nineteen ninety five; socialist, former French minister.
\item Revived European integration after ``Eurosclerosis'' of the nineteen seventies and early nineteen eighties.
\item Single market project, Single European Act, path to Maastricht, Schengen, cohesion policy; often seen as the architect of the relaunch.
\end{itemize}

\section*{6. Key readings in one or two lines}
\begin{itemize}
\item Zweig: describes a pre-war Europe that disappears; warns about nationalism, borders, and bureaucracy.
\item Judt: explains British ambivalence toward Europe; contrasts Europe with the Commonwealth; shows integration as messy and contingent.
\item Krawatzek and Pestel: argue for “new histories” that listen to local voices; criticise official pro-European narratives.
\item Anderson: discusses the democratic deficit and questions “ever closer union”; focuses on the role of courts and unelected institutions.
\item Vinen: presents “history in fragments”; argues that nineteen eighty nine did not simply unite Europe; highlights different “Europes”.
\item Bijsmans: shows Euroscepticism as a multifaceted phenomenon; distinguishes hard and soft Euroscepticism and different drivers.
\item Gilbert: warns against teleological histories that present integration as inevitable; emphasises losers, alternatives, and dead ends.
\item Kenny and Pearce: explore Brexit and the Anglosphere; show how Britain imagines a community beyond Europe.
\item Delors: Commission President nineteen eighty five to ninety five; revived integration after Eurosclerosis; associated with the Single European Act, Maastricht, Schengen, and cohesion.
\end{itemize}

\section*{7. Last-minute checklist}
\begin{itemize}
\item Can you draw the five-stage timeline and place Rome, the oil crisis, the Single European Act, Maastricht, and the two thousand eight crisis on it?
\item Can you explain in a few lines the differences between the Commission, the European Council, and the Council of the European Union?
\item Can you give short explanations of CAP, EMU, and the Green Deal?
\item Can you give one sentence on each main author: Zweig, Judt, Anderson, Vinen, Bijsmans, Gilbert, Kenny and Pearce?
\item Do you remember the answer structure: name, define, evidence, conclude?
\end{itemize}

\section*{8. Strategy recap}
\subsection*{What the exam is and is not}
\begin{itemize}
\item The exam is not a puzzle; it is not about trick questions; it is about whether you can read and analyse texts with an overview of the course.
\item Your job is to connect the text to the history, the institutions, the policies, and the readings you have already seen.
\item You should always think about: which stage of integration, which challenge, and which response.
\end{itemize}

\subsection*{Dimensions of integration}
\begin{itemize}
\item Economic dimension: most complete: customs union, single market, euro, common policies.
\item Political dimension: more integration but strong role for member states and vetoes.
\item Military and foreign policy dimension: clear limits, because of NATO, national sovereignty, and different traditions.
\item In answers, show which dimension the text is about and how far integration goes in that area.
\end{itemize}

\subsection*{How to answer like your professor}
\begin{itemize}
\item Always start by naming the concept, treaty, institution, or author.
\item Define it clearly in one sentence.
\item Give two or three specific pieces of evidence from the text: dates, quotes, or examples.
\item Finish with a short conclusion that answers the question directly and links back to the bigger course themes.
\end{itemize}

\section*{9. Historiography and teleology}
\begin{itemize}
\item Teleology in history means telling the story as if the end result was always meant to happen. In this course you are asked to avoid that.
\item Instead, stress contingency: actors in the past did not know the outcome; there were many possible paths and failures.
\item Official histories “for Europe” often present integration as a success story led by elites; the readings invite you to look also at dissent, colonialism, losers, and forgotten alternatives.
\item When you analyse a text, you can ask yourself whether it sounds like an official teleological story or a critical, contingent one.
\end{itemize}

\section*{10. Euroscepticism}
\begin{itemize}
\item Euroscepticism in the course is not just “anti-EU”; it is a multifaceted phenomenon with different types and motivations.
\item Hard Euroscepticism means rejecting the European Union and even wanting withdrawal; soft Euroscepticism accepts membership but criticises policies or specific directions.
\item A key phrase is the move from “permissive consensus” to “constraining dissensus” around the time of Maastricht: citizens became less willing to give elites a free hand.
\item Drivers include economics (winners versus losers), identity, and perceptions of democratic deficit.
\item There is a difference between constructive scepticism that pushes for reform with facts, and destructive scepticism that delegitimises and uses scapegoats.
\end{itemize}

\section*{11. Text analysis tips}
\begin{itemize}
\item Your job is to analyse, not to summarise everything. Focus on the main idea and argument.
\item Ask: what is the central claim of this text? What argument or logic supports it? What is one key expression that captures it?
\item Then connect the text to course themes: for example history versus institutions, supranational versus intergovernmental, official story versus critical story, centre versus periphery.
\item You do not need to memorise every date. You need to show that you understand how the text fits into the larger picture of European integration.
\end{itemize}

\subsection*{Example exam themes: Ribera, von der Leyen, Costa}
\begin{itemize}
\item Ribera versus von der Leyen: public disagreement on the Middle East; Ribera argued that ``respect for international law is a basic premise'' and that von der Leyen seemed to question it; raises who speaks for Europe and EU unity.
\item International law: rules states agree to follow; UN Charter, Geneva Conventions; post-nineteen forty-five order.
\item Multilateralism: many countries working together; opposite of unilateral action; creates balanced agreements.
\item Costa text: defended multilateralism and criticised one-sided US policy; example of EU united against US threats (e.g. Greenland); theme that Europe must act together, not just follow another power.
\item These examples link to Block two (institutions: who speaks for the EU?) and Block four (foreign and security policy).
\end{itemize}

\subsection*{Turkey and other candidate debates}
\begin{itemize}
\item Arguments for Turkish accession: strategic location, bridge to the Middle East, security, democracy catalyst.
\item Arguments against: cultural and religious differences, Cyprus obstacle, most of Turkey in Asia, human rights concerns especially under Erdogan; negotiations frozen.
\item Atatürk secularised Turkey; debate is old but current leaders and rule of law keep it on hold.
\end{itemize}

\subsection*{Common traps to avoid}
\begin{itemize}
\item Do not just summarise the text; analyse it and place it in the course.
\item Do not ignore the question; answer what is asked (context, key terms, comparison).
\item Do not write a generic answer; use the text and give specific evidence (dates, quotes, examples).
\item Do not forget to conclude: one or two lines that link back to the question and to the bigger themes (peace, prosperity, democracy, integration).
\end{itemize}
\section*{12. Detailed unit summaries from the midterm guide}

\subsection*{Unit 0: Course and assessment}
\begin{itemize}
\item Midterm: in-person, two or three open questions, short texts; your task is to analyse the main idea, argument, and key expression, not to summarise everything.
\item Essay: around three thousand five hundred words, topic agreed with the professor, with a balanced argument.
\item Presentations: two readings per session, focused on debate and participation.
\item Context: the European Union is in a tense moment and European history is full of crises; the course often compares Europe with the United States, China, and Russia.
\item Final exam: in May, cumulative, with emphasis on the later units.
\end{itemize}

\subsection*{Unit 1: Four blocks}
\begin{itemize}
\item Block one, history and origins: Schuman, Rome, the origins of the common market and money; logic and milestones rather than memorising every date.
\item Block two, institutions: “even more complex” in the professor’s words; includes executive, legislative, judiciary, and other bodies.
\item Block three, policies: euro, identity, enlargement, migration; especially relevant for exam questions.
\item Block four, foreign and security policy: Common Foreign and Security Policy and the external role of the EU.
\end{itemize}

\subsection*{Unit 2: Key concepts}
\begin{itemize}
\item Supranational: above the national level; EU institutions that can take binding decisions over member states.
\item Intergovernmental: cooperation between sovereign states that keep their veto power.
\item Official story: the pro-integration narrative that presents the EU as a success story of peace, unity, and progress.
\item Critical view: emphasises contingency and crises; integration is not inevitable; there were alternatives and dissenting voices.
\item Theory versus practice: theories describe ideal types; in practice politics and institutions are messy; the course asks you to look at practice.
\end{itemize}

\subsection*{Unit 3: History milestones}
\begin{itemize}
\item Nineteen forty five to nineteen fifty four: Marshall Plan, OEEC, Council of Europe, NATO, ECSC, and the failed European Defence Community; France blocked a supranational army.
\item Schuman Plan in nineteen fifty: coal and steel under a common High Authority; this is a core founding myth of the EU.
\item Treaty of Paris in nineteen fifty one: creates the ECSC with six members; first major supranational institution.
\item Treaty of Rome in nineteen fifty seven: creates the EEC and Euratom; sets up the customs union and the common market.
\item Empty chair crisis and Luxembourg Compromise: France withdraws from the Council, then secures the “vital national interest” veto; this produces paralysis.
\item Nineteen sixty seven and sixty eight: institutions are merged; the customs union is completed.
\item Hague Summit in nineteen sixty nine: sets a new agenda with enlargement and Economic and Monetary Union.
\item Nineteen seventy three: first enlargement; the UK, Ireland, and Denmark join; Norway votes no; EFTA continues as a free-trade alternative.
\item Oil crisis in nineteen seventy three: OPEC weapon; no common EEC energy response.
\item Southern enlargement: Greece in nineteen eighty one, Spain and Portugal in nineteen eighty six; democratisation and economic adjustment.
\item Single European Act: deepening the single market and extending qualified majority voting.
\item Maastricht: creates the EU, defines the euro path, adds three pillars and citizenship.
\item Schengen: removes internal borders for participating states.
\item Lisbon: adjusts the institutional balance and strengthens the Parliament.
\end{itemize}

\subsection*{Unit 4: Southern enlargement}
\begin{itemize}
\item Greece: Colonels’ dictatorship from nineteen sixty seven to seventy four; accession as democracy consolidation; Cyprus is part of the background.
\item Portugal: Carnation Revolution in nineteen seventy four; decolonisation; accession framed as democratic anchoring.
\item Spain: Franco dies in nineteen seventy five; negotiated transition; accession in nineteen eighty six; sports events and culture used as soft power.
\item Challenges: disputes around agricultural costs, fishing, steel, textiles, and the design of cohesion policy to help poorer regions.
\item Cohesion policy: structural funds, the European Investment Bank, the Committee of the Regions; all instruments for redistribution.
\item Gibraltar: closed border under Franco, reopened before accession; a specific issue in negotiations.
\end{itemize}

\subsection*{Unit 5: Institutions}
\begin{itemize}
\item Executive: European Council plus Commission; the “twin executive”; European Council gives general direction, Commission proposes and implements.
\item Legislative: Parliament plus Council of the EU; they share responsibility for passing laws.
\item Judiciary: Court of Justice; ensures the supremacy and uniform application of EU law.
\item Other bodies: European Central Bank, Court of Auditors, agencies such as the EU Intellectual Property Office.
\item A simple way to remember: Council plus Commission for the executive, Parliament plus Council for the legislative, Court of Justice for judiciary, and ECB and Auditors for money and control.
\end{itemize}

\subsection*{Unit 6: Readings and ideas}
\begin{itemize}
\item Zweig: the “world of yesterday” that disappears; after the First World War Europe is full of borders, xenophobia, and bureaucracy; tension between freedom and security.
\item Judt: British identity rooted in the Commonwealth and in victory in the Second World War; explains reluctance toward European integration.
\item Krawatzek and Pestel: criticise top-down, pro-European histories and call for more attention to local and dissenting voices.
\item Anderson: analyses the democratic deficit and the power of the Court of Justice and other unelected bodies; questions the meaning of “ever closer union”.
\item Vinen: “history in fragments” and “many Europes”; warns against simple unifying stories about nineteen eighty nine.
\item Bijsmans: offers a framework to understand Euroscepticism as hard or soft, driven by economic, identity, or democratic concerns.
\item Gilbert: warns against teleological success stories; asks historians to look at losers and failed projects.
\item Kenny and Pearce: focus on Brexit and the Anglosphere; explain how some in the UK imagine their community beyond Europe.
\end{itemize}

\end{document}

