% MidTerm Course Feedback: Product Management 2025--2026
% Compile with: pdflatex midterm-course-feedback-2025-2026.tex

\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{enumitem}
\setlist{nosep,leftmargin=*}
\usepackage{microtype}
\usepackage{amssymb}

\title{MidTerm Course Feedback: Product Management 2025--2026}
\author{}
\date{}

\begin{document}
\maketitle

\noindent Thanks for reading this. I answered as honestly as I could. One part is a little silly (the diaper lab) but I mean it in a good way.

\section*{1.\ My Major is\ldots}

\textbf{Computer Science.} I am at UCM this semester on study abroad.

\medskip
\noindent\textbf{On a scale of 1--5, how much did this course help you understand what a Product Manager actually does day-to-day?}\\
\textit{(1 = still confused, 5 = very clear picture)}

\medskip
\noindent\textbf{Rating: 4}

\medskip
\noindent\textbf{Please elaborate:}\\
A PM is not only ideas. They talk to users. They work with the business side. They work with the people who build the product. I get that better now. The canvas work, the Zara case, and design thinking helped me match class to my real job. I work in product at a health tech startup. I understand more than before. I still do not know everything. So I picked 4 not 5.

\medskip
\noindent\textit{(1 = irrelevant for my Major, 5 = extremely important for my Major)}

\medskip
\noindent\textbf{Rating: 5}

\medskip
\noindent\textbf{Please elaborate:}\\
Even for CS you need to know how products work. I do not only want to code alone at a desk. I want to know how teams choose what to build first. My job is product at a health tech company. So this class matched my real life. It was not extra fluff for me.

\section*{2.\ What was your favorite topic or activity?}

My favorite was the \textbf{diaper lab}. We went outside. We poured water in until the diapers \textbf{leaked}. It sounds funny. I still remember it. It showed why you test things for real, not only on a slide.

I also liked design thinking and the IDEO-style parts. I liked the \textbf{Business Model Canvas}. I liked the \textbf{piano / manufacturing} memo. I never thought a factory line could be a product choice before. That part changed my mind.

\section*{3.\ Workload balance (lectures, in-class tasks, homework)}

\textbf{[$\checkmark$] A good mix of both.}

\medskip
\noindent\textbf{Please elaborate:}\\
We had some lecture. We had some work in class. We had homework. It felt fair. The homework did not eat my whole week.

I have \textbf{ADHD}. Sometimes my brain wanders for a few seconds. That is on me. It is not because you teach badly. You actually explain things in a simple way. It is kind of like listening to a podcast. Your English is very clear. That helps me a lot.

\medskip
\noindent\textit{(I did not select the other two workload options.)}

\section*{4.\ Confidence working on a real-world product team after this class}

\textit{(5 = yes, definitely / 1 = not yet)}

\medskip
\noindent\textbf{Rating: 5}

\medskip
\noindent\textbf{Brief comment:}\\
I feel braver than week one. I am not perfect yet. I already work on a \textbf{real product team} at a health tech startup on the product side. Now I have words for stuff I was already seeing at work. That helped. I still get nervous when I have to explain hard choices out loud. I got \textbf{7.5} on the midterm. I have a lot going on this semester. I am happy with that grade.

\section*{5.\ One change + recommendation}

\noindent\textbf{If you could change one thing:}\\
I like the class. I would not rip it apart. One small thing would help me. Please put each \textbf{week's big due dates and topic in one easy spot}. Top of Moodle or first slide is fine. I have ADHD. I can miss something you said out loud even if I was sitting there. If it is written in one place I do not lose it. If it is easy, a short outline \textit{before} class helps too. Then if I zone out for 30 seconds I can catch up. This is not a complaint. It is just a wish.

\medskip
\noindent\textbf{Would you recommend this course to future students?}\\
\textit{(1 = not at all; 5 = for sure)}

\medskip
\noindent\textbf{Rating: 5}

\vspace{1em}
\noindent\textit{Jade}

\end{document}
