% Management in Global Markets – Closed-Notes Midterm (Week 8)
% Text-to-speech friendly version (simple sections, no columns or math symbols)

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=2cm]{geometry}
\usepackage{enumitem}
\setlist{nosep,leftmargin=1.5em}
\raggedright

\begin{document}

\section*{Management in Global Markets Closed-Notes Midterm (Week 8)}

Goal for each answer in the exam:
\begin{itemize}
\item First, say the name of the concept.
\item Second, define it in one clear short sentence.
\item Third, give one concrete example from class, a slide, or a case.
\item Fourth, explain in one line why this concept matters for internationalization.
\end{itemize}

\section*{1. Internationalization basics}
\begin{itemize}
\item International business means operating across borders with products, services, capital, or people.
\item Main reasons to go abroad: to reach bigger markets, to access resources, to become more efficient, and to learn from other contexts.
\item Main failure reasons discussed: choosing the wrong location, having a weak competitive advantage, or executing badly.
\item Key phrase from class: “Location is the masterpiece” – the choice of place can make or break the project.
\end{itemize}

\section*{2. Complexity and specialization}
\begin{itemize}
\item Economic complexity means moving from simple raw products to more complex products that require skills and know-how.
\item The realistic goal is to be very good at something specific in a specific place, not good at everything everywhere.
\item If the product is too complex for customers to understand, it becomes very hard to sell, even if it is technically strong.
\end{itemize}

\section*{3. Resources, capabilities, and competitive advantage}
\begin{itemize}
\item Resources are what the company has, such as assets, people, and brand.
\item Capabilities are what the company does with those resources, such as processes and routines.
\item Competitive advantage means being clearly better than rivals in some dimension; absolute advantage is rare.
\item Before going abroad you need to check honestly if your competitive advantage is strong enough, otherwise internationalization is very risky.
\end{itemize}

\section*{4. Four phases and location risk}
\begin{itemize}
\item Phase one is to conceive the project: plan the move and research the market.
\item Phase two is to execute: invest, move, and open plants or operations; this stage has the highest investment and risk.
\item Phase three is to establish: stabilise operations and reach profitability; this is the most dangerous phase because many projects fail here.
\item Phase four is to expand: grow once the model works well.
\item If you choose the wrong location in phase two or three, you can fail even if everything else looks good.
\end{itemize}

\section*{5. Culture and risks}
\begin{itemize}
\item Culture shock usually has three moments: first enthusiasm, then difficulties, and finally adaptation.
\item Artificial risk comes from laws and rules; you can manage it by learning and complying.
\item Natural risk comes from language and culture; you cannot escape it, so you must adapt.
\item Central sentence from class: you cannot escape language; communication problems destroy many international projects.
\end{itemize}

\section*{6. Human resources, training, and motivation}
\begin{itemize}
\item Skills can be developed through training or by hiring people who already have them.
\item Training formats mentioned: classroom teaching, discussions, conferences, and business games.
\item Job rotation in big companies means moving people between finance, production, and sales so they understand how the whole business works.
\item Motivation is essential; if people are not motivated, training does not turn into results.
\item Good habit: asking questions; it is not weakness, it is how you avoid expensive mistakes.
\end{itemize}

\section*{7. Export, international operations, and foreign direct investment}
\begin{itemize}
\item Export means the product moves to other countries but production stays at home.
\item International operations mean the company moves plants or key functions abroad.
\item Foreign Direct Investment is a long-term commitment of capital and people in another country and increases the complexity of human resources management.
\end{itemize}

\section*{8. Macro blocks and current context}
\begin{itemize}
\item Economic blocks discussed in class: the European Union with twenty seven countries, the United States, an Asia block such as ASEAN, and a South American block in discussion.
\item Europe depends a lot on imported energy; price shocks have a strong effect on companies and households.
\item Permanent members of the United Nations Security Council mentioned: the United States, China, Russia, France, and the United Kingdom.
\item Blocks and alliances are one way for countries to survive and compete in trade and politics.
\end{itemize}

\section*{9. Economic integration and regions}
\begin{itemize}
\item Economic integration means countries agree to remove barriers to trade in goods, services, people, and capital, and sometimes to share policies and a currency.
\item Static effects: what changes immediately when tariffs and barriers go to zero between two countries, such as more trade and specialisation.
\item Dynamic effects: longer‑term changes when neighbours trade and invest heavily in each other, such as shared supply chains, higher skills, and more complex products.
\item Example from class: central European countries like Switzerland and its neighbours trade and produce together; all are rich and highly complex, even if some have no natural resources.
\item Dumping: selling products abroad at artificially low prices to gain market share; it is considered unfair because it damages competitors who follow normal rules.
\item The European Union is not yet a full economic and monetary union like the United States; twenty seven countries share a market and a currency for many of them, but still keep many national policies.
\item Future potential members such as Ukraine must meet both economic and political conditions; war and institutional problems are major obstacles.
\end{itemize}

\section*{10. Quick definitions to memorise}
\begin{itemize}
\item Globalization: freer movement of goods, services, capital, and sometimes people; highly interconnected economies.
\item Slowbalization: slowing down of globalization and more protectionism and localisation.
\item Supply chain: the sequence of steps and locations that parts go through before becoming a final product.
\item Localization: adapting a product or service to the specific needs of a local market before or during expansion abroad.
\end{itemize}

\section*{11. Exam format reminders}
\begin{itemize}
\item You will have open questions, sometimes based on a slide with a graph or drawing, and space to write short answers by hand.
\item The professor expects clear, short lines, not long essays; one strong line is better than a page of vague text.
\item There are no multiple choice questions; you have to explain concepts in your own words.
\item If you can name the concept, define it, give one example, and link it to internationalization or economic integration, you are doing exactly what he wants.
\end{itemize}

\end{document}

