% Strategic Management — Exam One-Pager (derived from UCM materials)
% Compile with: pdflatex strategic-midterm-onepager.tex
\documentclass[9pt,landscape,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.8cm]{geometry}
\usepackage{multicol}
\usepackage{enumitem}
\setlist{nosep,leftmargin=*}
\usepackage{xcolor}
\definecolor{eublue}{RGB}{0,51,153}
\pagestyle{empty}
\begin{document}
\small
\begin{center}
{\large\bfseries\color{eublue} Strategic Management — Exam One‑Pager}\[0.2em]
\end{center}
\vspace{0.3em}
\begin{multicols}{3}

\section*{Master Pattern}
From a \textbf{[framework]} perspective, \textbf{[force/concept]} is \textbf{high/low} because \textbf{[reason]}, which makes the industry \textbf{[attractive/unattractive]} for \textbf{[who]}; therefore \textbf{[strategic implication]}.\\

\section*{Openers / Stock phrases}
\begin{itemize}
  \item "This question is essentially about \textbf{[topic]}."
  \item "From a \textbf{Porter Five Forces} perspective..."
  \item "Using the \textbf{resource‑based view (VRIO)}..."
  \item "At the \textbf{macro} level (PESTEL)..."
\end{itemize}

\section*{Frameworks — Quick checks}
\textbf{Five Forces:} Rivalry, entrants, buyers, suppliers, substitutes.\\
\textbf{VRIO:} Valuable? Rare? Inimitable? Organised?\\
\textbf{PESTEL:} Political, Economic, Social, Technological, Environmental, Legal.

\section*{Grant's 4 (case template)}
1) Goals. 2) Environment. 3) Resources/VRIO. 4) Implementation. Use as outline for every case.

\section*{SWOT (do it right)}
Link specific internal attributes to concrete external trends; each point → implication for advantage.

\section*{Porter: generic strategies}
Low‑cost / Differentiation / Focus. Avoid "stuck in the middle".

\columnbreak

\section*{High‑yield insights}
\begin{itemize}
  \item Intangibles (brand, routines, human capital) often explain sustained advantage beyond accounts.
  \item Industry unattractive but firm advantaged if VRIO resources offset industry forces.
  \item Clusters modify industry economics via proximity, shared suppliers and knowledge flows.
\end{itemize}

\section*{Common exam mistakes}
\begin{itemize}
  \item Listing instead of arguing. Always link cause → effect → implication.
  \item Using generic SWOT points with no link to CA.
  \item Mixing up por/para (note: not language exam — focus on strategy clarity).
\end{itemize}

\section*{Performance: Compared to what?}
Always benchmark: industry average, main rival, past performance, or firm goals.

\section*{Quick formulas}
Cost of equity (CAPM): $R_f + \beta( R_m - R_f)$ — use to discuss opportunity cost if relevant.

\columnbreak

\section*{Emergency checklist (when stuck)}
\begin{enumerate}
  \item Write one opener: name the topic.
  \item Pick one framework and say it.
  \item Choose 2–3 strong points and apply the Master Pattern.
  \item Close with one clear recommendation line.
\end{enumerate}

\section*{6 Rapid practice prompts}
\begin{enumerate}
  \item Industry attractiveness for airlines (Five Forces + VRIO example).
  \item RBV: How a firm can win in an unattractive industry.
  \item SWOT for a café vs delivery platforms (link to CA).
  \item Diversification recommendation (use BCG + related/unrelated logic).
  \item Buyer/supplier power in smartphone supply chain; recommend moves.
  \item Responding to an emerging substitute (master pattern + implementation risk).
\end{enumerate}

\section*{Exam timing tips}
Outline: 5 mins. Structure + points: 10–15 mins. Flesh and example: remaining time. Always leave 2–3 mins to conclude.

\section*{Closing line templates}
"In summary, these elements \underline{increase/reduce} profit potential and imply the firm should \underline{[recommendation]}."

\end{multicols}
\end{document}
