% Strategic Management: Week 9
% Compile: pdflatex starbucks-case.tex

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1.2cm]{geometry}
\usepackage{enumitem}
\setlist{nosep,leftmargin=*}
\usepackage{xcolor}
\usepackage{marginnote}
\usepackage{fancyhdr}
\usepackage{microtype}

\definecolor{eublue}{RGB}{0,51,153}
\definecolor{notepink}{RGB}{200,0,90}
\definecolor{softgrey}{RGB}{240,240,240}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[L]{\small Strategic Mgmt | Week 9}
\fancyfoot[R]{\small\thepage}
\raggedright

\newcommand{\handnote}[1]{%
  \par\noindent\footnotesize\color{notepink}\textit{#1}\par%
  \vspace{0.25em}%
}
\newcommand{\hlpink}[1]{\colorbox{pink!25}{\textbf{#1}}}

\newcommand{\answerbox}[1]{%
  \par\noindent\fcolorbox{eublue}{softgrey}{%
    \parbox{\dimexpr\linewidth-2\fboxsep-2\fboxrule}{#1}%
  }\par%
}

\begin{document}
\begin{center}
{\large\bfseries\color{eublue} Strategic Management -- Starbucks Case}\\[0.2em]
\footnotesize Mar 23, 2026 (Week 9). Break-down of what is going on + how to argue it in class.
\end{center}
\vspace{0.6em}

\section*{\color{eublue}1. Case in one paragraph (what is going on)}
Starbucks is used as a ``live'' case for how a firm turns an initial popular offer into a repeatable system that can be scaled across locations and time. The key strategic tension is not only ``how did growth happen?'' but also ``what lets the firm keep its advantage after competitors react and markets change?'' The case points to sustained success coming from a business model that stays consistent in the customer value delivered, while still adapting continuously in execution (operations, experience, and fit to markets).

\section*{\color{eublue}2. Strategy breakdown (mechanisms)}
\begin{enumerate}
  \item \textbf{Repeatable business model execution.}
  \begin{itemize}
    \item Store-level operations are designed so that the customer experience is recognizable across locations.
    \item Brand consistency and product/service delivery act like a ``system'' rather than a collection of isolated moves.
  \end{itemize}

  \item \textbf{Growth logic: scale without losing identity.}
  \begin{itemize}
    \item Expansion works when the company can replicate not just the stores, but the routines behind them (training, standards, and coordination).
    \item The advantage is reinforced as learning accumulates through operations at scale.
  \end{itemize}

  \item \textbf{Continuous adaptation (not one-time success).}
  \begin{itemize}
    \item The firm sustains growth by updating what it offers and how it delivers value as customer behavior and competitive conditions evolve.
    \item Adaptation is framed as changing ``implementation'' while protecting the core differentiators (what customers come for).
  \end{itemize}

  \item \textbf{Reinvention / turnaround logic (when performance is threatened).}
  \begin{itemize}
    \item When the original momentum is challenged, the strategy focuses on rebuilding store execution and restoring the customer experience.
    \item The lesson: advantage renewal requires active management choices, not automatic defense.
  \end{itemize}

  \item \textbf{International scaling logic.}
  \begin{itemize}
    \item The brand and system travel, but local markets require adaptation in how the offer is positioned and executed.
    \item Sustained growth depends on turning local expansion into repeatable learning that strengthens execution over time.
  \end{itemize}
 \end{enumerate}

\section*{\color{eublue}3. Map the case to course frameworks (how to argue)}
\subsection*{\color{eublue}A. RBV / VRIO (internal explanation)}
\begin{enumerate}
  \item \textbf{Value (V).} The Starbucks system delivers recognizable customer value (experience + consistency), which supports demand and long-term profitability.
  \item \textbf{Rarity (R).} It is not only ``a coffee shop''; it is the combination of brand, operations, and customer-experience routines that is harder to find as a single package.
  \item \textbf{Inimitability (I).} Competitors can imitate products quickly, but copying the full operating system (training + routines + standards + brand experience) is slower and culturally embedded.
  \item \textbf{Non-substitutability (N).} Customers may substitute coffee, but it is harder to substitute the specific ``repeatable experience'' with a simple alternative without losing what they value.
  \item \textbf{Organization (O).} The firm must be organized to exploit the resources (execution standards, capability building, and management discipline across locations).
\end{enumerate}

\subsection*{\color{eublue}B. Competitive advantage as a renewal problem}
The case pushes the idea that competitive advantage must be renewed: rivalry and imitation gradually erode early wins, so sustained advantage depends on continual improvements while protecting core differentiators.

\subsection*{\color{eublue}C. Value chain (where the execution happens)}
\begin{itemize}
  \item \textbf{Inbound logistics:} ensure consistent input quality (coffee sourcing and standards).
  \item \textbf{Operations:} turn the brand promise into store routines (how the product and service are delivered).
  \item \textbf{Marketing \& sales / service:} reinforce the experience and make the offering recognizable.
  \item \textbf{Supporting activities:} HR/training and coordination capabilities that scale the system across geographies.
\end{itemize}

\section*{\color{eublue}4. Risks and counter-arguments (what could break the advantage)}
\begin{enumerate}
  \item \textbf{Commoditization of products.} If coffee itself becomes easier to match, differentiation must shift to experience and execution.
  \item \textbf{Experience drift at scale.} Expansion can create inconsistency if training/standards weaken.
  \item \textbf{Competitive response.} Rivals can copy surface features; sustained advantage requires deeper operational coherence.
  \item \textbf{Market saturation / cost pressure.} Growth may slow if expansion opportunities diminish or costs rise.
\end{enumerate}

\section*{\color{eublue}5. What to say in class (speaking templates)}
\subsection*{\color{eublue}A. 60--90 seconds (oral answer skeleton)}
\begin{enumerate}
  \item \textbf{Opening.} Starbucks shows how a firm turns initial popularity into sustainable advantage through positioning, execution, and scaling.
  \item \textbf{Why it worked.} The business model was repeatable across locations, so customers received a consistent experience; operations and experience were managed as a system.
  \item \textbf{Why growth was sustained.} Growth came from continuous adaptation while protecting core differentiators; advantage had to be renewed, not only defended.
  \item \textbf{Close.} The main lesson is that competitive advantage must be actively renewed over time.
\end{enumerate}

\subsection*{\color{eublue}B. 30 seconds cold-call version (3 lines)}
\begin{enumerate}
  \item \textbf{Topic:} Starbucks shows how initial popularity becomes sustainable advantage.
  \item \textbf{Logic:} Repeatable business model + system execution + continuous adaptation.
  \item \textbf{Action/implication:} Advantage persists only if the firm renews execution as markets change.
\end{enumerate}

\section*{\color{eublue}6. Answers to the case questions (ready-to-say)}
% Note: wording of your case synopsis may vary slightly by edition. This matches the typical 3-part prompt shown in your `starbucks-1.JPG`.
% Key questions (as visible in `starbucks-1.JPG`):
% - "Why has Starbucks' strategy succeeded so well?"
% - "Is Starbucks' competitive advantage sustainable?"
% - "Give your reason."
% - Advice prompt: what Mr. Schultz should amend/refine in order to remain successful.

\subsection*{\color{eublue}Key quotes / phrases from your pages}
\begin{enumerate}
  \item ``The future''
  \item ``Rekindling growth''
  \item ``Crisis and renaissance''
  \item ``Acquiring coffee beans of a high, consistent quality''
  \item ``Employee involvement''
  \item ``Closing Case''
\end{enumerate}

\subsection*{\color{eublue}Q1. Why has Starbucks' strategy succeeded so well?}
Answer (based on your notes + what the reading labels):
\\
``POPULARITY BUILT THROUGH REPEATABLE BUSINESS MODEL EXECUTION.''
\\
``OPERATIONS + CUSTOMER EXPERIENCE WERE MANAGED AS A SYSTEM, NOT AS ISOLATED MOVES.''
\\
``GROWTH SUSTAINED THROUGH CONTINUOUS ADAPTATION, NOT ONE-TIME MOVE.''
\\
\\
\textbf{Unit 5 (Competitive Strategy) 5.4 alignment (framework lines):}
\\
``PRODUCT DIFFERENTIATION''
\\
``Product diff ≠ Price Premium''
\\
``Costs NOT ALWAYS → C.A.''
\\
\textbf{Proof from class notes (`2026-03-25-class-notes.md`):}
\\
``POPULARITY BUILT THROUGH REPEATABLE BUSINESS MODEL EXECUTION'' (II.A.1)
\\
``OPERATIONS + CUSTOMER EXPERIENCE WERE MANAGED AS A SYSTEM, NOT AS ISOLATED MOVES'' (IV.B.2)
\\
``GROWTH SUSTAINED THROUGH CONTINUOUS ADAPTATION, NOT ONE-TIME MOVE'' (II.A.2)
\\
\\
\textbf{Proof from reading pages (`starbucks-*.JPG`):}
\\
``The future'' (starbucks-2)
\\
``Closing Case'' (starbucks-5)
\\
``Acquiring coffee beans of a high, consistent quality'' (starbucks-5)
\\
``Employee involvement'' (starbucks-5)

\textbf{Proof from `sm-unit-5-competitive-strategy.pdf` (Unit 5, 5.4):}
\\
``PRODUCT DIFFERENTIATION''
\\
``Product diff ≠ Price Premium''
\\
``Costs NOT ALWAYS → C.A.''
\\
``Stuck in the “middle”?'' 

\subsection*{\color{eublue}Q2. Is Starbucks' competitive advantage sustainable? Why or why not?}
Answer (based on your notes + what the reading labels):
\\
``THE MAIN LESSON IS THAT COMPETITIVE ADVANTAGE MUST BE RENEWED, NOT JUST DEFENDED.''
\\
\textbf{Unit 5 (Competitive Strategy) 5.4 support (framework lines):}
\\
``Costs NOT ALWAYS → C.A.''
\\
``Stuck in the “middle”?'' 
\\
\\
\textbf{Proof from class notes (`2026-03-25-class-notes.md`):}
\\
``THE MAIN LESSON IS THAT COMPETITIVE ADVANTAGE MUST BE RENEWED, NOT JUST DEFENDED'' (IV.D.1)
\\
\\
\textbf{Proof from reading pages (`starbucks-*.JPG`):}
\\
``Crisis and renaissance'' (starbucks-4)
\\
``Rekindling growth'' (starbucks-3)
\\
\\
\textbf{Proof from `sm-unit-5-competitive-strategy.pdf` (Unit 5, 5.4):}
\\
``Costs NOT ALWAYS → C.A.''
\\
``Stuck in the “middle”?'' 

\subsection*{\color{eublue}Q3. If Starbucks wants to stay successful, what should it focus on next?}
Answer (next focus), using your notes as the “what to do”:
\\
``REVIEW FRAMEWORKS FOR SUSTAINING COMPETITIVE ADVANTAGE.''
\\
``PREPARE TO MAP CASE OBSERVATIONS TO COURSE MODELS.''
\\
\\
\textbf{Unit 6 (Corporate Strategy) 6.2 support (framework lines):}
\\
``Try to consolidate its position in the markets and strengthen its competitive position in the industry (lower costs or more value added).''
\\
``Considered as low risk strategy “always doing the same products for the same customers needs”''
\\
\textbf{Proof from class notes (`2026-03-25-class-notes.md`):}
\\
``REVIEW FRAMEWORKS FOR SUSTAINING COMPETITIVE ADVANTAGE'' (III.B.1)
\\
``PREPARE TO MAP CASE OBSERVATIONS TO COURSE MODELS'' (III.B.2)
\\
\\
\textbf{Proof from reading pages (`starbucks-*.JPG`):}
\\
``Closing Case'' (starbucks-5)
\\
``Acquiring coffee beans of a high, consistent quality'' (starbucks-5)
\\
``Employee involvement'' (starbucks-5)
\\
``Rekindling growth'' (starbucks-3)
\\
\\
\textbf{Proof from `sm-unit-6-corporate-strategy-development.pdf` (Unit 6, 6.2):}
\\
``Try to consolidate its position in the markets and strengthen its competitive position in the industry (lower costs or more value added).''
\\
``Considered as low risk strategy “always doing the same products for the same customers needs”''

\section*{\color{eublue}Inserted case text + highlights (from your pasted text)}
\subsection*{\color{eublue}Closing Case: Starbucks Corporation (pp. 144-148)}

\subsubsection*{\color{eublue}Background}
Coffee drinking spread from the Middle East/North Africa to Europe in the 16th-17th centuries. By the early 20th century it was a staple beverage across continental Europe and the Americas. Instant coffee in the 1950s further expanded the mass market. Against this backdrop, \hlpink{Howard Schultz} --- an appliance salesman from Brooklyn -- \hlpink{built a global chain worth \$52 billion}.

\handnote{Class tie: positioning/execution/scaling as sustained advantage after initial popularity (II.B.1 + II.B.2).}

\subsubsection*{\color{eublue}The Rise: Wake Up and Smell the Coffee}
\hlpink{Schultz joined Starbucks in 1982.} After a trip to Italy, he became convinced Starbucks could sell brewed coffee and recreate the Italian cafe experience --- not just coffee, but \hlpink{community}. When the owners resisted, he eventually acquired the business and expanded it.

His vision was a \hlpink{"third place"} --- between home and work --- built on:
\begin{itemize}
  \item \hlpink{High-quality coffee}: ethical sourcing, careful roasting, partnering with growers
  \item \hlpink{Employee involvement}: baristas were central to the experience; staff were treated as business partners with healthcare (even part-timers), training, and a culture of belonging
  \item \hlpink{Community \& social purpose}: Schultz wanted Starbucks to be a company people were proud of regardless of background
  \item \hlpink{Store design}: clean, distinctive aesthetic --- "the urban suavity of a neighbourhood combined with the crispness of the Pacific Northwest and the feel of a Milan espresso bar"
  \item \hlpink{Location strategy}: clustering ~20 stores per urban hub to build a "Starbucks buzz"; adding drive-throughs and highway-adjacent stores
\end{itemize}

\handnote{Class tie for Q1: \hlpink{POPULARITY BUILT THROUGH REPEATABLE BUSINESS MODEL EXECUTION} + \hlpink{OPERATIONS + CUSTOMER EXPERIENCE WERE MANAGED AS A SYSTEM}.}

\subsubsection*{\color{eublue}Results (1993-2007)}
\hlpink{Revenues grew from \$160M to \$9,412M}; expansion into \hlpink{51 countries}; operating margin of \hlpink{29\%}; return on equity of \hlpink{26.5\%}.

\subsubsection*{\color{eublue}Crisis and Renaissance}
Schultz stepped back as CEO in 2000. By 2007, same-store sales slowed, profits fell, and the share price dropped over \hlpink{75\%}. He returned as CEO in early 2008.

His \hlpink{turnaround strategy} included:
\begin{itemize}
  \item \hlpink{Closing 600 US stores; cutting 6,000 jobs; closing Australian stores}
  \item \hlpink{Returning to core values}: reformulated mission statement --- "to inspire and nurture the human spirit -- one person, one cup and one neighbourhood at a time"
  \item \hlpink{Replacing automated espresso machines with manual ones; removing breakfast sandwiches (their aroma masked the coffee smell)}
  \item \hlpink{Heavy use of social media \& mobile technology}, Facebook for community-building
  \item \hlpink{Pioneering mobile payments via Square partnership}
\end{itemize}

\handnote{Class tie for Q2: advantage must be \hlpink{RENEWED, NOT JUST DEFENDED} (IV.D.1) and growth must be \hlpink{CONTINUOUS ADAPTATION, NOT ONE-TIME MOVE} (II.A.2).}

\subsubsection*{\color{eublue}Rekindling Growth}
Once stabilized, growth resumed in two areas:
\begin{enumerate}
  \item \hlpink{Grocery trade}: products sold through supermarkets and retailers; new products like Via (instant coffee launched Feb 2009 at \$2.95/pack of 3), Seattle's Best, Tazo Teas. Via exceeded \$100M in sales in its first year.
  \item \hlpink{International markets}: \hlpink{China and India} as primary targets; China --- 1,500 stores in 70 cities by 2015; India --- 50/50 joint venture with Tata Group. Also acquired Evolution Fresh, Teavana, and La Boulange (2011-2012).
\end{enumerate}

\subsubsection*{\color{eublue}The Future (as of 2014-2015)}
Starbucks projected \hlpink{11\% annual revenue growth} and \hlpink{14\% earnings growth}. However, analysts questioned the \hlpink{long-term sustainability} given:
\begin{itemize}
  \item competition from independent cafes and chains
  \item McDonald's McCafes and fast-food chains adding premium coffee
  \item premium roasters competing directly (Lavazza, Illy, Segafredo Zanetti)
  \item growth of home-brewing (Nespresso pod systems)
  \item questions about whether diversification into tea, juice, instant coffee, and grocery trade fit Starbucks' core mission and capabilities
\end{itemize}

\handnote{Class tie for Q3/Q4: tie "next focus" to \hlpink{continuous adaptation} + \hlpink{sustaining competitive advantage} (II.A + III.B).}

\subsection*{\color{eublue}Case Questions (as in your pasted text)}
\begin{enumerate}
  \item \hlpink{Summarize Starbucks' strategy in 2014.} \handnote{Proof frame: positioning/execution/scaling + repeatable model execution (II.B.1 + II.A.1).}
  \item \hlpink{Why has Starbucks' strategy succeeded so well?} \handnote{Proof: \hlpink{POPULARITY BUILT THROUGH REPEATABLE BUSINESS MODEL EXECUTION} + \hlpink{OPERATIONS + CUSTOMER EXPERIENCE WERE MANAGED AS A SYSTEM}.}
  \item \hlpink{Is Starbucks' competitive advantage sustainable? Give your reasons.} \handnote{Proof: \hlpink{THE MAIN LESSON IS THAT COMPETITIVE ADVANTAGE MUST BE RENEWED, NOT JUST DEFENDED}.}
  \item \hlpink{Advise Mr. Schultz on whether and how Starbucks should amend its strategy to remain successful.} \handnote{Proof frame: \hlpink{REVIEW FRAMEWORKS FOR SUSTAINING COMPETITIVE ADVANTAGE} + map observations to course models (III.B).}
\end{enumerate}

\section*{\color{eublue}Case Answers (highlight + pink margin notes)}

\subsection*{\color{eublue}1. Summarize Starbucks' strategy in 2014}
\answerbox{From the case, Starbucks' strategy is built on the \hlpink{"third place"} concept: a community space between home and work centered on \hlpink{high-quality, hand-crafted coffee} and \hlpink{employee involvement}. Growth then continues through \hlpink{international markets} with \hlpink{China and India} as primary targets, alongside \hlpink{grocery trade} sold through \hlpink{supermarkets and retailers} (including \hlpink{Via} and other packaged products). The reading also includes \hlpink{retail diversification} through acquisitions such as \hlpink{Evolution Fresh, Teavana, and La Boulange} and highlights \hlpink{digital engagement} via \hlpink{social media \& mobile technology} and \hlpink{mobile payments}.}
\handnote{Class proof: \hlpink{POPULARITY BUILT THROUGH REPEATABLE BUSINESS MODEL EXECUTION} + \hlpink{OPERATIONS + CUSTOMER EXPERIENCE WERE MANAGED AS A SYSTEM}.}
\handnote{Class discussion cues (from transcript keywords): ``drivers''; ``atmosphere/community''; ``third place''; ``employee involvement''; ``clustering of stores and cities''.}

\subsection*{\color{eublue}2. Why has Starbucks' strategy succeeded so well?}
\answerbox{The reading attributes success to the foundations of the \hlpink{"third place"} experience (community between home and work) built on \hlpink{high-quality coffee} and \hlpink{employee involvement}, alongside \hlpink{store design} and \hlpink{location strategy} that creates dense local presence. It also frames the ability to sustain performance through \hlpink{Crisis and Renaissance} followed by \hlpink{Rekindling Growth}. Your class notes capture this as: \hlpink{POPULARITY BUILT THROUGH REPEATABLE BUSINESS MODEL EXECUTION}, \hlpink{OPERATIONS + CUSTOMER EXPERIENCE WERE MANAGED AS A SYSTEM}, and \hlpink{GROWTH SUSTAINED THROUGH CONTINUOUS ADAPTATION, NOT ONE-TIME MOVE}.}
\handnote{Proof from reading: \hlpink{"Crisis and Renaissance"} + \hlpink{"Rekindling Growth"}. Proof from class notes: the three exact phrases above.}
\handnote{Class discussion cues (from transcript keywords): ``main barriers''; ``high price''; ``perceived value''; ``McDonald's'' + ``Laza'' + ``Cafe'' (competition keywords).}

\subsection*{\color{eublue}3. Is Starbucks' competitive advantage sustainable? Give your reasons.}
\answerbox{In \hlpink{The Future (as of 2014-2015)}, the case says analysts questioned \hlpink{long-term sustainability} due to: \hlpink{competition from independent cafes and chains}, \hlpink{McDonald's McCafes and fast-food chains adding premium coffee}, and \hlpink{premium roasters competing directly} (Lavazza, Illy, Segafredo Zanetti), plus \hlpink{growth of home-brewing (Nespresso pod systems)}. It also questions whether diversification into \hlpink{tea, juice, instant coffee, and grocery trade} fits Starbucks' \hlpink{core mission and capabilities}. This matches your class lesson: \hlpink{THE MAIN LESSON IS THAT COMPETITIVE ADVANTAGE MUST BE RENEWED, NOT JUST DEFENDED}.}
\handnote{Proof from reading: the bullet list under \hlpink{The Future}. Proof from class notes: \hlpink{THE MAIN LESSON IS THAT COMPETITIVE ADVANTAGE MUST BE RENEWED, NOT JUST DEFENDED}.}
\handnote{Class discussion cues (from transcript keywords): ``substitution'' + ``home brewing''; ``coffee capsules''; ``substitute products''; ``invisibility of the products''.}

\subsection*{\color{eublue}4. Advise Mr. Schultz on whether and how Starbucks should amend its strategy to remain successful}
\answerbox{The case advice is grounded in two parts of the reading: (1) \hlpink{Crisis and Renaissance} actions and (2) the \hlpink{The Future} questions about mission fit. In \hlpink{Crisis and Renaissance}, the reading lists a \hlpink{turnaround strategy} that includes returning to \hlpink{core values} (including the reformulated mission statement), changing execution by \hlpink{replacing automated espresso machines with manual ones} and \hlpink{removing breakfast sandwiches}, and reinforcing community through \hlpink{social media \& mobile technology} and \hlpink{mobile payments} (Square partnership). In \hlpink{The Future}, it explicitly asks whether diversification into \hlpink{tea, juice, instant coffee, and grocery trade} fits Starbucks' \hlpink{core mission and capabilities}. Your class notes frame the goal as \hlpink{REVIEW FRAMEWORKS FOR SUSTAINING COMPETITIVE ADVANTAGE} and the logic that advantage must be \hlpink{RENEWED, NOT JUST DEFENDED}.}
\handnote{Proof from reading: \hlpink{Crisis and Renaissance} + \hlpink{The Future} diversification-fit question. Proof from class notes: \hlpink{THE MAIN LESSON IS THAT COMPETITIVE ADVANTAGE MUST BE RENEWED, NOT JUST DEFENDED} + \hlpink{REVIEW FRAMEWORKS FOR SUSTAINING COMPETITIVE ADVANTAGE}.}
\handnote{Class discussion cues (from transcript keywords): ``choice'' + ``justify''; ``main barriers''; ``in order to maintain these choices''.}

\end{document}

