% All Quick Notes -- One page per course (combined)
% Compile: pdflatex blue-notes-all.tex
% Print only the page you need: p.1=Spanish, p.2=Strategic, p.3=Product, p.4=Intro EU, p.5=Management Global

\documentclass[10pt,landscape,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage{amsmath}
\usepackage[left=1.2cm,right=1.2cm,top=1cm,bottom=1cm]{geometry}
\usepackage{multicol}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{booktabs}
\definecolor{accent}{RGB}{34,139,34}
\setlist{nosep,leftmargin=*,itemsep=0.2em}
\setlength{\parskip}{0.4em}
\setlength{\columnsep}{1em}
\raggedright

\begin{document}

% ----- PAGE 1: SPANISH -----
\begin{center}
{\LARGE\bfseries\color{accent} Spanish -- Quick Notes}\\[0.3em]
\small Page 1. Print this for Spanish exam.
\end{center}
\vspace{0.5em}
\begin{multicols}{2}
\subsection*{\color{accent} If they ask... $\to$ Think...}
\begin{itemize}[leftmargin=*,nosep]
\item \textbf{Por vs para?} Para + inf (purpose). Porque + verb (reason). Por + noun (for/because of).
\item \textbf{C o qu?} qu before e, i. qui\'en = qu (not q). 6 = seis (not sies).
\item \textbf{Nacionalidad?} Agreement m/f. -o/-a. -ista, -ense invariable.
\item \textbf{Pronunciaci\'on?} Carlos [k], Garc\'ia [g], Javier [x], Celia [s].
\item \textbf{Listening?} nombre, origen, nacionalidad, edad, profesi\'on.
\end{itemize}

\subsection*{\color{accent} Preguntas (match question $\to$ answer)}
\begin{center}
\small
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Pregunta} & \textbf{Respuesta} \\
\midrule
¿C\'omo te llamas? & Francisco / Me llamo... \\
¿Cu\'antos a\~nos tienes? & Treinta y cinco. \\
¿Cu\'al es tu apellido? & Mart\'inez. \\
¿De d\'onde eres? & De Valencia. \\
¿En qu\'e trabajas? & Soy camarero. \\
\bottomrule
\end{tabular}
\end{center}

\subsection*{\color{accent} Por vs Para vs Porque}
\begin{center}
\small
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Use} & \textbf{Example} \\
\midrule
Para + infinitive & para hablar, para practicar \\
Porque + clause & porque quiero ver \\
Por + noun & por la comida, por el K-pop \\
\bottomrule
\end{tabular}
\end{center}

\subsection*{\color{accent} Ser \& Tener}
Ser: soy, eres, es, somos, sois, son. Tener: tengo, tienes, tiene, tenemos, ten\'eis, tienen. Llamarse: me llamo, te llamas, se llama... \textbf{Agreement} with person (m/f).

\subsection*{\color{accent} N\'umeros}
0--15: cero, uno... cinco, \textbf{seis}, siete... quince. 16--19: diecis\'eis, diecisiete... 20--50: veinte, treinta, cuarenta, cincuenta.

\subsection*{\color{accent} 5 lenguas Espa\~na}
Espa\~nol, euskera, catal\'an, aran\'es, gallego. Rom\'anicas: esp, cat, gal, aran\'es. Euskera: origen incierto.

\subsection*{\color{accent} Actividades}
Ver: pel\'iculas, series. Escuchar: m\'usica, radio. Leer: libros. Escribir: diario. Practicar: con nativos, pronunciaci\'on. Hacer: ejercicios.

\subsection*{\color{accent} Pronunciaci\'on}
Carlos [k]: c before a,o,u; Q. Garc\'ia [g]: G before a,o,u. Javier [x]: J; G before e,i. Celia [s]: c before e,i; Z.

\subsection*{\color{accent} Listening -- Una fiesta}
Ana: not Argentina, not cocinera. Elvira: colombiana. Stephanie: not Dutch. Jos\'e Antonio: profesor de espa\~nol.

\subsection*{\color{accent} Common mistakes}
6 = seis. qui\'en = qu. Gapfill: check gender (mi amiga $\to$ -a).
\end{multicols}

\newpage
% ----- PAGE 2: STRATEGIC -----
\begin{center}
{\LARGE\bfseries\color{accent} Strategic Management -- Quick Notes}\\[0.3em]
\small Page 2. Define + example + tie to CA.
\end{center}
\vspace{0.5em}
\begin{multicols}{2}
\subsection*{\color{accent} If they ask... $\to$ Think...}
\begin{itemize}[leftmargin=*,nosep]
\item \textbf{Compare internal vs external?} Internal = RBV, resources, VRIO. External = PESTEL, Five Forces.
\item \textbf{CA in unattractive industry?} Strong internal (VRIO) can outweigh bad industry.
\item \textbf{Value in intangibles?} $\sim$70\%. Not in books. Human capital, reputation.
\item \textbf{Grant's four?} Goals $\to$ env $\to$ VRIO $\to$ implementation.
\item \textbf{Case (Madonna/Lola)?} Goals, env, resources, implementation. Reinvention vs identity+family.
\end{itemize}

\subsection*{\color{accent} Key definitions}
Strategy = long-term, scarce resources. Mission = who (current). Vision = where (future). Objectives = how. CA = customer chooses you. Know yourself, enemy, terrain.

\subsection*{\color{accent} Formula}
Cost of equity: $R_f + \beta(\text{Market} - R_f)$. Satisfied when return $>$ cost of equity. Compare vs industry.

\subsection*{\color{accent} Porter \& SWOT}
Porter: low-cost, diff, focus. \textbf{Never stuck in the middle.} SWOT: S/W = internal. O/T = external. \textbf{Be specific.}

\subsection*{\color{accent} Resources vs Capabilities}
\begin{center}
\small
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Resources} & \textbf{Capabilities} \\
\midrule
What you \textit{have} & What you \textit{do} \\
Assets, people, brand & Processes, routines \\
\bottomrule
\end{tabular}
\end{center}

\subsection*{\color{accent} PESTEL}
Political, Economic, Social, Technological, Ecological, Legal. One example each. Strong change $\to$ new O \& T.

\subsection*{\color{accent} Five Forces}
Rivalry, New entrants, Substitutes, Buyer power, Supplier power. Strong = bad. Pick 2--3. Industry + firm effect. Attractive = O $>$ T.

\subsection*{\color{accent} VRIO}
Valuable, Rare, Inimitable, Non-substitutable + \textbf{Organisation}. All 4 + Org = sustained CA. Have vs do. 70--80\% = you.

\subsection*{\color{accent} Tangible vs Intangible}
Intangible: human capital, reputation. $\sim$70\% value. Not in books. Double loss when people leave.

\subsection*{\color{accent} Madonna vs Lola}
Both = human resources. Madonna: reinvention, differentiation. Lola: identity + family. Grant's four applies.

\subsection*{\color{accent} Common mistakes}
Stuck in the middle. Vague SWOT. Forgetting Organisation in VRIO.
\end{multicols}

\newpage
% ----- PAGE 3: PRODUCT MGMT -----
\begin{center}
{\LARGE\bfseries\color{accent} Product Management -- Quick Notes}\\[0.3em]
\small Page 3. Tie to value creation/capture.
\end{center}
\vspace{0.5em}
\begin{multicols}{2}
\subsection*{\color{accent} If they ask... $\to$ Think...}
\begin{itemize}[leftmargin=*,nosep]
\item \textbf{Create vs capture?} Creation = value for users. Capture = money. Takeda. Market access.
\item \textbf{Cost vs price?} Cost = what you spend. Price = what you choose. Low cost $\neq$ low price.
\item \textbf{Why product fail?} No market fit, no willingness to pay, wrong community, didn't validate.
\item \textbf{Kodak?} Film $\to$ digital. Innovator's dilemma. Didn't adapt.
\item \textbf{Design thinking?} Observe, don't ask. Empathize $\to$ Define $\to$ Ideate $\to$ Prototype $\to$ Test.
\item \textbf{BMC?} 9 blocks. Validate before build. Customer discovery.
\end{itemize}

\subsection*{\color{accent} Value creation vs capture}
\begin{center}
\small
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{} & \textbf{Creation} & \textbf{Capture} \\
\midrule
What & Total value for users & Money you make \\
Depends on & Product, usefulness & Market access, patents, brand \\
\bottomrule
\end{tabular}
\end{center}
\textbf{Takeda}: Spanish 15K $\to$ Takeda 250M. Market access, distribution, scale. Co-specialized assets. Teece.

\subsection*{\color{accent} Big ideas}
Community before product. Don't build and hope. Willingness to pay: test early. Cost $\neq$ price. Validate before build.

\subsection*{\color{accent} BMC}
9 blocks. Customer segments, value prop, channels, key resources. Lean. Customer discovery. Validate first.

\subsection*{\color{accent} Exploration vs exploitation}
Ambidextrous org. Sensing vs seizing. SDLC. Both needed.

\subsection*{\color{accent} Design thinking}
Observe, don't ask. Gemba. Extreme users. 5 stages: Empathize $\to$ Define $\to$ Ideate $\to$ Prototype $\to$ Test.

\subsection*{\color{accent} Cost}
Fixed vs variable. Economies of scale. Henry Ford. Mass production. Standardization.

\subsection*{\color{accent} Innovation}
S-curve. Disruptive tech. Kodak: film $\to$ digital fail. Innovator's dilemma. First mover risk.

\subsection*{\color{accent} Common mistakes}
Creation $\neq$ capture. Building before validating. Ignoring willingness to pay.
\end{multicols}

\newpage
% ----- PAGE 4: INTRO EU -----
\begin{center}
{\LARGE\bfseries\color{accent} Introduction to EU -- Quick Notes}\\[0.3em]
\small Page 4. Analyse, don't summarise.
\end{center}
\vspace{0.5em}
\begin{multicols}{2}
\subsection*{\color{accent} If they ask... $\to$ Think...}
\begin{itemize}[leftmargin=*,nosep]
\item \textbf{Main idea?} Central argument. Don't summarise everything.
\item \textbf{What are they arguing?} Logic. Cause \& effect.
\item \textbf{Key expression?} Quote that captures the argument.
\item \textbf{Official vs critical?} Official = success, unity. Critical = contingency, crises.
\item \textbf{Milestones?} Schuman $\to$ Rome $\to$ Luxembourg $\to$ Southern $\to$ Maastricht.
\end{itemize}

\subsection*{\color{accent} Task}
\textbf{Analyse}, don't summarise. Main idea. Argument. Key expression. 2--3 open questions. Connect to course themes.

\subsection*{\color{accent} Concepts}
Supranational vs intergovernmental. Official story vs critical view. Theory $\neq$ practice. Four blocks: history, institutions, policies, foreign.

\subsection*{\color{accent} Milestones (order)}
Schuman (1950) $\to$ Rome (1957) $\to$ Empty chair (1965) $\to$ Luxembourg (1966) $\to$ Hague (1969) $\to$ 1973 (UK, Ire, DK) $\to$ Oil crisis $\to$ Southern (Greece 1981, Spain \& Portugal 1986) $\to$ SEA (1986) $\to$ Maastricht (1992) $\to$ Schengen $\to$ Lisbon (2007)

\subsection*{\color{accent} Key facts}
1945--54: Marshall, OEEC, Council of Europe, NATO, ECSC, EDC failed. 1973: Norway no (fishing). Oil: OPEC weapon, stagflation. Southern: Greece (colonels), Spain (Franco, 1982 World Cup), Portugal (Carnation). Cohesion: structural funds, EIB. Gibraltar: border 1969--82. Commission proposes. Council decides. France + Germany = engine.

\subsection*{\color{accent} Institutions}
Executive: Council + Commission. Legislative: Parliament + Council. Judiciary: Court of Justice. Other: ECB, Auditors.

\subsection*{\color{accent} Readings}
Zweig (borders, freedom vs security). Judt (British reluctance). Anderson (democratic deficit). Vinen (fragments). Bijsmans (Euroscepticism). Delors. Teleology. Histories ``for'' Europe.

\subsection*{\color{accent} Euroscepticism}
Hard vs soft. Permissive consensus $\to$ constraining dissensus. Drivers: economic, identity, democratic.

\subsection*{\color{accent} Common mistakes}
Summarising instead of analysing. Forgetting key expression. Ignoring official vs critical.
\end{multicols}

\newpage
% ----- PAGE 5: MANAGEMENT GLOBAL -----
\begin{center}
{\LARGE\bfseries\color{accent} Management Global Markets -- Quick Notes}\\[0.3em]
\small Page 5. Tie to internationalization.
\end{center}
\vspace{0.5em}
\begin{multicols}{2}
\subsection*{\color{accent} If they ask... $\to$ Think...}
\begin{itemize}[leftmargin=*,nosep]
\item \textbf{Why fail abroad?} Wrong location, weak CA, Phase 2--3, tech transfer, culture.
\item \textbf{Strategy levels?} Corporate, competitive, functional.
\item \textbf{Export vs int'l?} Export = product moves. Int'l = company moves. FDI = next step.
\item \textbf{Resources vs capabilities?} Have vs do. Table.
\item \textbf{Four phases?} Conceive $\to$ Execute (critical) $\to$ Establish (dangerous) $\to$ Expand.
\item \textbf{Why competitors?} Validation, infrastructure, learn. Go where they are.
\end{itemize}

\subsection*{\color{accent} Resources vs Capabilities}
\begin{center}
\small
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Aspect} & \textbf{Resources} & \textbf{Capabilities} \\
\midrule
What & What you \textit{have} & What you \textit{do} \\
Examples & Assets, people, brand & Processes, routines \\
\bottomrule
\end{tabular}
\end{center}

\subsection*{\color{accent} Big ideas}
Location = masterpiece. Most fail. Global vs slowbalization. China = exporter, USA = importer. Go where competitors are. Culture shock: honeymoon $\to$ hard $\to$ adapt. Hofstede: power distance, individualism, long-term.

\subsection*{\color{accent} Four phases}
Conceive (2--3y) $\to$ Execute (critical, wrong place = fail) $\to$ Establish (most dangerous) $\to$ Expand. Total 4--5y. Phase 3 = most fail.

\subsection*{\color{accent} Chile case}
French $\to$ Chile. Tech transfer risk. Partners used tech independently. Communication broke. No protection.

\subsection*{\color{accent} Export vs Internationalization}
Export = product moves, low risk. Int'l = company moves, plants abroad. FDI = long-term. Domestic vs international vs transnational.

\subsection*{\color{accent} Strategy \& SME}
Corporate (which businesses), competitive (how to compete), functional (HR, marketing). SME: $<$250 emp, $<$50M. Before abroad: strong CA?

\subsection*{\color{accent} Why fail}
Wrong location, weak CA, poor execution, tech transfer risk, culture, Phase 2--3, left alone.

\subsection*{\color{accent} Common mistakes}
Ignoring location. Going alone. Skipping Phase 2 due diligence.
\end{multicols}

\end{document}
