% Introduction to EU -- One-page quick notes
% Compile: pdflatex intro-eu-only.tex
% Print this page only for Intro EU exam

\documentclass[10pt,landscape,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage[left=1.2cm,right=1.2cm,top=1cm,bottom=1cm]{geometry}
\usepackage{multicol}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{booktabs}
\definecolor{accent}{RGB}{34,139,34}
\setlist{nosep,leftmargin=*,itemsep=0.2em}
\setlength{\parskip}{0.4em}
\setlength{\columnsep}{1em}
\raggedright

\begin{document}
\normalsize

\begin{center}
{\LARGE\bfseries\color{accent} Introduction to EU -- Quick Notes}\\[0.3em]
\small One page. Analyse, don't summarise.
\end{center}
\vspace{0.5em}

\begin{multicols}{2}

\subsection*{\color{accent} If they ask... $\to$ Think...}
\begin{itemize}[leftmargin=*,nosep]
\item \textbf{Main idea?} Central argument. Don't summarise everything.
\item \textbf{What are they arguing?} Logic. Cause \& effect.
\item \textbf{Key expression?} Quote that captures the argument.
\item \textbf{Official vs critical?} Official = success, unity. Critical = contingency, crises.
\item \textbf{Milestones?} Schuman $\to$ Rome $\to$ Luxembourg $\to$ Southern $\to$ Maastricht.
\end{itemize}

\subsection*{\color{accent} Task}
\textbf{Analyse}, don't summarise. Main idea. Argument. Key expression. 2--3 open questions. Connect to course themes.

\subsection*{\color{accent} Concepts}
Supranational vs intergovernmental. Official story vs critical view. Theory $\neq$ practice. Four blocks: history, institutions, policies, foreign.

\subsection*{\color{accent} Milestones (order)}
Schuman (1950) $\to$ Rome (1957) $\to$ Empty chair (1965) $\to$ Luxembourg (1966) $\to$ Hague (1969) $\to$ 1973 (UK, Ire, DK) $\to$ Oil crisis $\to$ Southern (Greece 1981, Spain \& Portugal 1986) $\to$ SEA (1986) $\to$ Maastricht (1992) $\to$ Schengen $\to$ Lisbon (2007)

\subsection*{\color{accent} Key facts}
1945--54: Marshall, OEEC, Council of Europe, NATO, ECSC, EDC failed. 1973: Norway no (fishing). Oil: OPEC weapon, stagflation. Southern: Greece (colonels), Spain (Franco, 1982 World Cup), Portugal (Carnation). Cohesion: structural funds, EIB. Gibraltar: border 1969--82. Commission proposes. Council decides. France + Germany = engine.

\subsection*{\color{accent} Institutions}
Executive: Council + Commission. Legislative: Parliament + Council. Judiciary: Court of Justice. Other: ECB, Auditors.

\subsection*{\color{accent} Readings}
Zweig (borders, freedom vs security). Judt (British reluctance). Anderson (democratic deficit). Vinen (fragments). Bijsmans (Euroscepticism). Delors. Teleology. Histories ``for'' Europe.

\subsection*{\color{accent} Euroscepticism}
Hard vs soft. Permissive consensus $\to$ constraining dissensus. Drivers: economic, identity, democratic.

\subsection*{\color{accent} Common mistakes}
Summarising instead of analysing. Forgetting key expression. Ignoring official vs critical.
\end{multicols}
\end{document}
