% Management Global Markets -- One-page quick notes
% Compile: pdflatex management-global-only.tex
% Print this page only for Management Global exam

\documentclass[10pt,landscape,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage[left=1.2cm,right=1.2cm,top=1cm,bottom=1cm]{geometry}
\usepackage{multicol}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{booktabs}
\definecolor{accent}{RGB}{34,139,34}
\setlist{nosep,leftmargin=*,itemsep=0.2em}
\setlength{\parskip}{0.4em}
\setlength{\columnsep}{1em}
\raggedright

\begin{document}
\normalsize

\begin{center}
{\LARGE\bfseries\color{accent} Management Global Markets -- Quick Notes}\\[0.3em]
\small One page. Define + example + tie to internationalization.
\end{center}
\vspace{0.5em}

\begin{multicols}{2}

\subsection*{\color{accent} If they ask... $\to$ Think...}
\begin{itemize}[leftmargin=*,nosep]
\item \textbf{Why fail abroad?} Wrong location, weak CA, Phase 2--3, tech transfer, culture.
\item \textbf{Strategy levels?} Corporate, competitive, functional.
\item \textbf{Export vs int'l?} Export = product moves. Int'l = company moves. FDI = next step.
\item \textbf{Resources vs capabilities?} Have vs do. Table.
\item \textbf{Four phases?} Conceive $\to$ Execute (critical) $\to$ Establish (dangerous) $\to$ Expand.
\item \textbf{Why competitors?} Validation, infrastructure, learn. Go where they are.
\end{itemize}

\subsection*{\color{accent} Resources vs Capabilities}
\begin{center}
\small
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Aspect} & \textbf{Resources} & \textbf{Capabilities} \\
\midrule
What & What you \textit{have} & What you \textit{do} \\
Examples & Assets, people, brand & Processes, routines \\
\bottomrule
\end{tabular}
\end{center}

\subsection*{\color{accent} Big ideas}
Location = masterpiece. Most fail. Global vs slowbalization. China = exporter, USA = importer. Go where competitors are. Culture shock: honeymoon $\to$ hard $\to$ adapt. Hofstede: power distance, individualism, long-term.

\subsection*{\color{accent} Four phases}
Conceive (2--3y) $\to$ Execute (critical, wrong place = fail) $\to$ Establish (most dangerous) $\to$ Expand. Total 4--5y. Phase 3 = most fail.

\subsection*{\color{accent} Chile case}
French $\to$ Chile. Tech transfer risk. Partners used tech independently. Communication broke. No protection.

\subsection*{\color{accent} Export vs Internationalization}
Export = product moves, low risk. Int'l = company moves, plants abroad. FDI = long-term. Domestic vs international vs transnational.

\subsection*{\color{accent} Strategy \& SME}
Corporate (which businesses), competitive (how to compete), functional (HR, marketing). SME: $<$250 emp, $<$50M. Before abroad: strong CA?

\subsection*{\color{accent} Why fail}
Wrong location, weak CA, poor execution, tech transfer risk, culture, Phase 2--3, left alone.

\subsection*{\color{accent} Common mistakes}
Ignoring location. Going alone. Skipping Phase 2 due diligence.
\end{multicols}
\end{document}
