% Product Management -- One-page quick notes
% Compile: pdflatex product-mgmt-only.tex
% Print this page only for Product Management exam

\documentclass[10pt,landscape,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage[left=1.2cm,right=1.2cm,top=1cm,bottom=1cm]{geometry}
\usepackage{multicol}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{booktabs}
\definecolor{accent}{RGB}{34,139,34}
\setlist{nosep,leftmargin=*,itemsep=0.2em}
\setlength{\parskip}{0.4em}
\setlength{\columnsep}{1em}
\raggedright

\begin{document}
\normalsize

\begin{center}
{\LARGE\bfseries\color{accent} Product Management -- Quick Notes}\\[0.3em]
\small One page. Define + example + tie to value creation/capture.
\end{center}
\vspace{0.5em}

\begin{multicols}{2}

\subsection*{\color{accent} If they ask... $\to$ Think...}
\begin{itemize}[leftmargin=*,nosep]
\item \textbf{Create vs capture?} Creation = value for users. Capture = money. Takeda. Market access.
\item \textbf{Cost vs price?} Cost = what you spend. Price = what you choose. Low cost $\neq$ low price.
\item \textbf{Why product fail?} No market fit, no willingness to pay, wrong community, didn't validate.
\item \textbf{Kodak?} Film $\to$ digital. Innovator's dilemma. Didn't adapt.
\item \textbf{Design thinking?} Observe, don't ask. Empathize $\to$ Define $\to$ Ideate $\to$ Prototype $\to$ Test.
\item \textbf{BMC?} 9 blocks. Validate before build. Customer discovery.
\end{itemize}

\subsection*{\color{accent} Value creation vs capture}
\begin{center}
\small
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{} & \textbf{Creation} & \textbf{Capture} \\
\midrule
What & Total value for users & Money you make \\
Depends on & Product, usefulness & Market access, patents, brand \\
\bottomrule
\end{tabular}
\end{center}
\textbf{Takeda}: Spanish 15K $\to$ Takeda 250M. Market access, distribution, scale. Co-specialized assets. Teece.

\subsection*{\color{accent} Big ideas}
Community before product. Don't build and hope. Willingness to pay: test early. Cost $\neq$ price. Validate before build.

\subsection*{\color{accent} BMC}
9 blocks. Customer segments, value prop, channels, key resources. Lean. Customer discovery. Validate first.

\subsection*{\color{accent} Exploration vs exploitation}
Ambidextrous org. Sensing vs seizing. SDLC. Both needed.

\subsection*{\color{accent} Design thinking}
Observe, don't ask. Gemba. Extreme users. 5 stages: Empathize $\to$ Define $\to$ Ideate $\to$ Prototype $\to$ Test.

\subsection*{\color{accent} Cost}
Fixed vs variable. Economies of scale. Henry Ford. Mass production. Standardization.

\subsection*{\color{accent} Innovation}
S-curve. Disruptive tech. Kodak: film $\to$ digital fail. Innovator's dilemma. First mover risk.

\subsection*{\color{accent} Common mistakes}
Creation $\neq$ capture. Building before validating. Ignoring willingness to pay.
\end{multicols}
\end{document}
