% Strategic Management -- One-page quick notes
% Compile: pdflatex strategic-only.tex
% Print this page only for Strategic exam

\documentclass[10pt,landscape,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage[left=1.2cm,right=1.2cm,top=1cm,bottom=1cm]{geometry}
\usepackage{multicol}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{booktabs}
\definecolor{accent}{RGB}{34,139,34}
\setlist{nosep,leftmargin=*,itemsep=0.2em}
\setlength{\parskip}{0.4em}
\setlength{\columnsep}{1em}
\raggedright

\begin{document}
\normalsize

\begin{center}
{\LARGE\bfseries\color{accent} Strategic Management -- Quick Notes}\\[0.3em]
\small One page. Define + example + tie to CA.
\end{center}
\vspace{0.5em}

\begin{multicols}{2}

\subsection*{\color{accent} If they ask... $\to$ Think...}
\begin{itemize}[leftmargin=*,nosep]
\item \textbf{Compare internal vs external?} Internal = RBV, resources, VRIO. External = PESTEL, Five Forces.
\item \textbf{CA in unattractive industry?} Strong internal (VRIO) can outweigh bad industry.
\item \textbf{Value in intangibles?} $\sim$70\%. Not in books. Human capital, reputation.
\item \textbf{Grant's four?} Goals $\to$ env $\to$ VRIO $\to$ implementation.
\item \textbf{Case (Madonna/Lola)?} Goals, env, resources, implementation. Reinvention vs identity+family.
\end{itemize}

\subsection*{\color{accent} Key definitions}
Strategy = long-term, scarce resources. Mission = who (current). Vision = where (future). Objectives = how. CA = customer chooses you. Know yourself, enemy, terrain.

\subsection*{\color{accent} Formula}
Cost of equity: $R_f + \beta(\text{Market} - R_f)$. Satisfied when return $>$ cost of equity. Compare vs industry.

\subsection*{\color{accent} Porter \& SWOT}
Porter: low-cost, diff, focus. \textbf{Never stuck in the middle.} SWOT: S/W = internal. O/T = external. \textbf{Be specific.}

\subsection*{\color{accent} Resources vs Capabilities}
\begin{center}
\small
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Resources} & \textbf{Capabilities} \\
\midrule
What you \textit{have} & What you \textit{do} \\
Assets, people, brand & Processes, routines \\
\bottomrule
\end{tabular}
\end{center}

\subsection*{\color{accent} PESTEL}
Political, Economic, Social, Technological, Ecological, Legal. One example each. Strong change $\to$ new O \& T.

\subsection*{\color{accent} Five Forces}
Rivalry, New entrants, Substitutes, Buyer power, Supplier power. Strong = bad. Pick 2--3. Industry + firm effect. Attractive = O $>$ T.

\subsection*{\color{accent} VRIO}
Valuable, Rare, Inimitable, Non-substitutable + \textbf{Organisation}. All 4 + Org = sustained CA. Have vs do. 70--80\% = you.

\subsection*{\color{accent} Tangible vs Intangible}
Intangible: human capital, reputation. $\sim$70\% value. Not in books. Double loss when people leave.

\subsection*{\color{accent} Madonna vs Lola}
Both = human resources. Madonna: reinvention, differentiation. Lola: identity + family. Grant's four applies.

\subsection*{\color{accent} Common mistakes}
Stuck in the middle. Vague SWOT. Forgetting Organisation in VRIO.
\end{multicols}
\end{document}
