% Introduction to the EU - Week 9 Reading Summary
% Compile: pdflatex 8a-Court-of-justice-reading-summary.tex

\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=2.5cm]{geometry}
\usepackage{booktabs}
\usepackage{enumitem}
\setlist{nosep,leftmargin=*}
\usepackage{parskip}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{xcolor}
\definecolor{eublue}{RGB}{0,51,153}

\hypersetup{
  colorlinks=true,
  linkcolor=eublue,
  urlcolor=eublue,
  pdftitle={8a Court of Justice Reading Summary},
  pdfauthor={Introduction to the EU, UCM}
}

\begin{document}

\title{8a Court of Justice\\Reading Summary (Working Draft)}
\author{Introduction to the European Union\\Universidad Complutense de Madrid\\Week 9}
\date{}
\maketitle
\vspace{-1em}
\hrule
\vspace{1em}

\section*{Bibliographic Information}
\begin{itemize}
\item \textbf{Source file:} 8a Court of justice.pdf
\item \textbf{Author:} [OCR NEEDED]
\item \textbf{Title (full):} [OCR NEEDED]
\item \textbf{Year:} [OCR NEEDED]
\end{itemize}

\section*{Extraction Note}
The PDF appears image-based in this repository snapshot (no selectable text in direct extraction).
Use OCR (or classroom copy) to fill exact quotations and page-accurate references.

\section*{High-Confidence Topic Frame (from class context)}
\begin{itemize}
\item Court of Justice role in ensuring interpretation/application of EU law.
\item Primacy and direct effect as foundations of legal integration.
\item Preliminary ruling system as link between EU and national courts.
\item Tension between supranational authority and national constitutional limits.
\end{itemize}

\section*{Summary Skeleton (to complete after OCR)}
\subsection*{I. Institutional Role}
\begin{itemize}
\item Mandate under treaties: [ADD EXACT WORDING]
\item Relationship with national judiciaries: [ADD]
\end{itemize}

\subsection*{II. Core Doctrines}
\begin{itemize}
\item Primacy: [ADD]
\item Direct effect: [ADD]
\item Judicial review scope: [ADD]
\end{itemize}

\subsection*{III. Limits And Reform Questions}
\begin{itemize}
\item Current constraints on jurisdiction: [ADD]
\item Potential reforms discussed: [ADD]
\end{itemize}

\section*{Discussion Prompts}
\begin{enumerate}
\item How does the text define the Court's role in balancing integration and member-state sovereignty?
\item Which legal tools most effectively secure uniform EU law application?
\item Where are the practical limits of judicial authority in politically sensitive fields?
\end{enumerate}

\vspace{1em}
\noindent\footnotesize\textit{Introduction to the European Union, Universidad Complutense de Madrid.}

\end{document}
