% Introduction to the EU ... Week 9 Housing Crisis Workshop
% Compile: pdflatex eu-housing-crisis-workshop.tex

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1.2cm]{geometry}
\usepackage{enumitem}
\setlist{nosep,leftmargin=*}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage{microtype}
\usepackage{hyperref}

\definecolor{eublue}{RGB}{0,51,153}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[L]{\small Intro EU | Week 9}
\fancyfoot[R]{\small\thepage}
\raggedright

\hypersetup{
  colorlinks=true,
  urlcolor=eublue,
}

\begin{document}
\begin{center}
{\large\bfseries\color{eublue} Introduction to the EU ... Week 9}\\[0.2em]
\footnotesize Mar 23. Housing crisis workshop (European Parliament ... group debate)
\end{center}\vspace{0.5em}

\section*{\color{eublue}TL;DR (what to produce)}
\begin{itemize}
\item For each political group, write down their \textbf{housing language}, the \textbf{tools they push}, their \textbf{stance on the EU's role}, and what they want to \textbf{move forward vs stop} in the debate.
\item Use Europarl (housing search + statements/debates). Keep it short: turn what you find into clear note-lines.
\item Connect to the Vienna example: prevention logic, limited-profit/non-market housing associations (market-damping effect), public-housing scale, and what changes for affordability and family access.
\item Finish with a compare-and-explain: \textbf{3 similarities} + \textbf{3 differences} between groups, and \textbf{1 reason} for each difference (based on their wording/tools).
\end{itemize}
\noindent\textit{Reminder:} The HOUS output you are using is political direction/recommendations (non-legislative), so treat it as “what Parliament pushes for”, not as instantly binding EU law.

\section*{\color{eublue}Session readings (week-9 PDFs)}
\begin{itemize}
\item \texttt{7a Parlamentary Europe.pdf}
\item \texttt{7b Olsen European Parliament.pdf}
\item \texttt{European Parliament.pdf}
\end{itemize}

\section*{\color{eublue}Core resources (links)}
\begin{itemize}
\item Europarl housing search:
  \href{https://www.europarl.europa.eu/portal/en/search?planet=_all&searchQuery=housing}{https://www.europarl.europa.eu/portal/en/search?planet=_all\&searchQuery=housing}
\end{itemize}

\section*{\color{eublue}What to extract from Europarl (use their exact words)}
\begin{itemize}
\item \textbf{1 Europarl source link} for the debate/initiative you use (paste the URL in your notes).
\item \textbf{Parliament vocabulary}: the words they use to describe the problem and to argue for a certain approach.
\item \textbf{Lexicon + roots}: for each group, list the housing words they repeat most + the story they are telling about ``what the housing problem is''.
\item \textbf{Policy mechanisms} they emphasize (the ``how'': regulation, funding, targeting, public-housing logic, affordability rules, support for buyers, etc.).
\item \textbf{What goes through vs what gets stopped}: the language they use about what should \emph{pass} and what should be \emph{blocked/skipped} in the debate flow.
\item \textbf{Debate output}: keep your summary tied to the exact statements you found (not generic textbook explanations).
\end{itemize}

\section*{\color{eublue}Housing issue map (pick 1 focus per group)}
\begin{itemize}
\item Supply side: \textbf{construction / new dwellings}, \textbf{housing inventory}, \textbf{planning & delivery}
\item Demand side: \textbf{affordability}, \textbf{rents / prices}, \textbf{buyer access} (first-time buyers, families)
\item Social impact: \textbf{social / public housing}, \textbf{vulnerable groups}, \textbf{homelessness}
\item Market design: \textbf{rental regulation}, \textbf{tax rules}, \textbf{subsidies / targeted support}
\item Governance frame: \textbf{EU competence} (what the EU can/cannot do), \textbf{subsidiarity logic}, \textbf{who implements}
\end{itemize}

\section*{\color{eublue}Workshop workflow (do this in order)}
\begin{enumerate}
\item Pick a housing-related Europarl initiative / debate item from the link above.
\item Identify the \textbf{political groups} involved (who speaks / which positions appear).
\item For each group, extract 4 outputs (lexicon, tools, EU-role stance, procedure logic).
\item Prepare short group presentations (use note-lines + 1 quote slot if possible): \textbf{about 45 minutes total for group work}, then share findings.
\end{enumerate}

\section*{\color{eublue}Use their exact words (no guessing)}
\begin{itemize}
\item \textbf{Lexicon / framing}: 3--5 key terms + one sentence that captures what they think the housing problem is.
\item \textbf{Policy tools}: 1--2 emphasized mechanisms (public housing, regulation, funding, targeting, buyer support, tax rules, etc.).
\item \textbf{EU role stance}: pro-EU / cautious / skeptical (include \emph{one phrase} they actually use).
\item \textbf{Debate flow}: what they say should \emph{pass} vs what should be \emph{blocked/skipped}.
\end{itemize}

\section*{\color{eublue}Quote slots (paste exact sentences)}
\begin{itemize}
\item Quote (Group: \texttt{EPP}): ``The report places housing supply at the core of the response, recognising the need to enable the delivery of around 10 million additional homes across Europe.'' \hfill (Borja Gim\'enez Larraz, 9 Feb 2026; HOUS report Europarl link)
\item Quote (Group: \texttt{S\&D}): ``This is a social emergency. Between 2010 and 2024, house prices in the European Union have increased by 53\% and rents by 25\%.'' \hfill (Aodh\'an \'O R\'iord\'ain, S\&D housing negotiator)
\item Quote (Group: \texttt{Renew}): ``We must bridge the investment gap by mobilizing private capital and removing the tax barriers that prevent young Europeans from buying their first home; the Single Market is our strongest tool for affordability.'' \hfill (Ciar\'an Mullooly, Renew Europe Vice-Chair, HOUS Committee Debate, 9 Feb 2026)
\item Quote (Group: \texttt{Greens/EFA}): ``The EU must put people's right to housing before profit.'' \hfill (Greens/EFA housing page you used)
\item Quote (Group: \texttt{The Left}): ``We are building a Europe where housing is a fundamental right, not a speculative asset.'' \hfill (The Left housing justice page you used)
\item Quote (Group: \texttt{ECR}): ``Housing is and must remain a national competence. The EU's role is not to regulate rents, but to simplify rules so that property owners and builders can actually provide the supply our citizens need.'' \hfill (ECR Group Statement on the adoption of the Gim\'enez Larraz report, Feb 2026)
\item Quote (Group: \texttt{PfE}): ``Brussels should stop imposing 'Green' mandates that drive up renovation costs for families. We need a housing policy that respects national sovereignty and protects the traditional family home.'' \hfill (Patriots for Europe (PfE) spokesperson, Europarl press room, 10 Feb 2026)
\item Quote (Group: \texttt{ESN}): ``The EU budget is being wasted on bureaucratic prestige projects while our citizens cannot afford to live in their own cities. We demand the redirection of funds to national housing priorities, not supranational experiments.'' \hfill (Europe of Sovereign Nations (ESN) Group news bulletin, Feb 2026)
\item Quote (Group: \texttt{Non-Inscrits}): ``The report before us fails to address the unique demographic crises of the Member States, offering only a one-size-fits-all 'European' solution that satisfies no one.'' \hfill (Independent MEP statement during the HOUS plenary, 9 Feb 2026)
\end{itemize}

\section*{\color{eublue}Vienna housing link (how to connect)}
\begin{itemize}
\item \textbf{Prevention logic}: avoid secondary/undesired effects.
\item \textbf{Limited-profit/non-market housing associations}: prevention before speculation starts.
\item \textbf{Market-damping effect}: a large non-market stock keeps private rents lower (for everyone, not only tenants of public housing).
\item \textbf{Public housing requirement scale} (as in class example): approx. 1940s $\sim$50\%; center areas $\sim$70\% to $\sim$50\%.
\item \textbf{Effects}: price + family access (what changes for who?)
\end{itemize}

\section*{\color{eublue}Political spectrum snapshot (10th EP) ... compare stances}
\begin{itemize}
\item EPP Group (baseline label): Christian democracy / conservatism; centre-right (use this only as context).
\item S\&D Group (baseline label): social democracy; centre-left (use this only as context).
\item Renew Group (baseline label): liberalism; centre to centre-right (use this only as context).
\item Greens/EFA Group (baseline label): green politics; centre-left to left-wing (use this only as context).
\item The Left Group (baseline label): democratic socialism; left-wing (use this only as context).
\item ECR Group (baseline label): national conservatism / right-wing populism (use this only as context).
\item PfE Group (baseline label): right-wing populism (use this only as context).
\item ESN Group (baseline label): far-right / ultraconservative (use this only as context).
\item Non-Inscrits (baseline label): not in a political group (use this only as context).
\end{itemize}

\section*{\color{eublue}Required source log (one Europarl item per group)}
\begin{itemize}
\item For each group you discuss, you must paste the exact Europarl link you used (debate/initiative + date + speaker if you can).
\end{itemize}
\begin{center}
\begin{tabular}{p{2.6cm} p{10.5cm}}
\textbf{Group} & \textbf{Europarl link (paste URL + item title)} \\
\hline
EPP & \texttt{https://www.europarl.europa.eu/news/en/press-room/20260205IPR33603/meps-adopt-proposals-to-tackle-europe-s-housing-crisis} (Borja Gim\'enez Larraz, 9 Feb 2026) \\
S\&D & \texttt{https://www.europarl.europa.eu/news/en/press-room/20260205IPR33603/meps-adopt-proposals-to-tackle-europe-s-housing-crisis} (Aodh\'an \'O R\'iord\'ain, S\&D housing negotiator) \\
Renew & \texttt{https://www.europarl.europa.eu/news/en/press-room/20260205IPR33603/meps-adopt-proposals-to-tackle-europe-s-housing-crisis} (Ciar\'an Mullooly, Renew, Vice-Chair of HOUS) \\
Greens/EFA & \texttt{https://www.europarl.europa.eu/news/en/press-room/20260205IPR33603/meps-adopt-proposals-to-tackle-europe-s-housing-crisis} (Benedetta Scuderi, Greens) \\
The Left & \texttt{https://www.europarl.europa.eu/news/en/press-room/20260205IPR33603/meps-adopt-proposals-to-tackle-europe-s-housing-crisis} (Leila Chaibi / The Left housing justice framing) \\
ECR & \texttt{https://www.europarl.europa.eu/news/en/press-room/20260205IPR33603/meps-adopt-proposals-to-tackle-europe-s-housing-crisis} (ECR national competence framing) \\
PfE & \texttt{https://www.europarl.europa.eu/news/en/press-room/20260205IPR33603/meps-adopt-proposals-to-tackle-europe-s-housing-crisis} (PfE national sovereignty framing) \\
ESN & \texttt{https://www.europarl.europa.eu/news/en/press-room/20260205IPR33603/meps-adopt-proposals-to-tackle-europe-s-housing-crisis} (ESN sovereignty/bureaucracy framing) \\
Non-Inscrits & \texttt{PV-10-2026-03-10 (paste HOUS minutes link) + speaker name + item/quote title} \\
\end{tabular}
\end{center}

\section*{\color{eublue}Group-by-group housing stance answers (fill-in template)}
\begin{itemize}
\item Instruction: don't guess. Copy their exact wording from the Europarl initiative/debate first, then compress it into short note-lines.
\item Output per group (repeat 1 template per group):
  \begin{itemize}
  \item (0) Where you got it: Europarl link + speaker/date (paste exact URL).
  \item (1) Housing framing / lexicon: 3--5 key words + 1 sentence framing.
  \item (2) Proposed tools: 1--2 mechanisms they emphasize (state-led, market-led, mixed; targeting; regulation; funding; etc.).
  \item (3) EU role stance: pro-EU / cautious / skeptical (justify with 1 quote/phrase + link).
  \item (4) Debate procedure logic: what they say should pass vs what should be blocked/skipped (based on their wording).
  \end{itemize}
\end{itemize}

\subsection*{\color{eublue}Template by group (write during the workshop)}
\begin{itemize}
\item EPP Group:
  \begin{itemize}
  \item (0) Source (Europarl link + speaker/date): \texttt{https://www.europarl.europa.eu/news/en/press-room/20260205IPR33603/meps-adopt-proposals-to-tackle-europe-s-housing-crisis} (Borja Gim\'enez Larraz, 9 Feb 2026)
  \item (1) Lexicon + framing:
  supply; investment; simplification; private property; legal certainty.
  ``Problem is insufficient housing supply caused by too much regulation and bureaucracy.''
  \item (2) Tools:
  administrative simplification (planning-permit speed); tax incentives for buyers; EU cohesion funding to boost construction; public-private partnerships.
  \item (3) EU role stance:
  cautious/supportive: EU as facilitator/catalyst (removes obstacles, facilitates investment). Not a regulator of markets.
  \item (4) Procedure logic:
  wants supply-side measures to pass; blocks rent controls (``ineffective''), redistribution measures, and strong anti-speculation rules.
  \end{itemize}
\item S\&D Group:
  \begin{itemize}
  \item (0) Source (Europarl link + speaker/date): use the HOUS report Europarl link above; S\&D framing (Aodh\'an \'O R\'iord\'ain, S\&D housing negotiator).
  \item (1) Lexicon + framing:
  affordable housing; social emergency; public housing; tenants' rights; speculation; social good.
  ``Homes have become profit-driven assets instead of a social right for everyone.''
  \item (2) Tools:
  EU funding for affordable/public housing; regulation of short-term rentals; tenants' rights protection; targeting vulnerable and middle-income groups.
  \item (3) EU role stance:
  pro-EU; brought housing to the forefront and pushed for the special committee / dedicated housing delegation in the Commission.
  \item (4) Procedure logic:
  wants earmarked EU funding to pass; accepted compromise on the final report; blocks pure market-only approaches.
  \end{itemize}
\item Renew Group:
  \begin{itemize}
  \item (0) Source (Europarl link + speaker/date): use the HOUS report Europarl link above; Renew framing (Ciar\'an Mullooly, Renew, Vice-Chair of HOUS).
  \item (1) Lexicon + framing:
  investment; market efficiency; single market; affordability; first-time buyers.
  ``Supply/investment gap: the market can fix it with the right conditions.''
  \item (2) Tools:
  remove tax barriers for first-time buyers; EU investment instruments (EIB); incentive-based tax; balance tourism and housing affordability via short-term rental rules.
  \item (3) EU role stance:
  pro-EU as coordinator: supports EU investment and rules to improve market functioning, not to replace the market.
  \item (4) Procedure logic:
  supports investment-led approach; blocks regulatory/rent-control measures.
  \end{itemize}
\item Greens/EFA:
  \begin{itemize}
  \item (0) Source (Europarl link + speaker/date): use the HOUS report Europarl link above; Greens/EFA framing (Benedetta Scuderi, Greens).
  \item (1) Lexicon + framing:
  right to housing; speculation; profit; renovictions; Housing First; public housing; sustainability.
  ``Speculation/short-term rentals/underinvestment in public housing drive up costs.''
  \item (2) Tools:
  EU investment to close the €57 billion yearly housing gap; Housing First for homelessness; stop renovictions; regulate short-term rentals; renovation support for vulnerable households.
  \item (3) EU role stance:
  pro-EU intervention: ``The EU must put people's right to housing before profit.''
  \item (4) Procedure logic:
  strongly criticised the final HOUS direction and pushed for stronger anti-speculation rules and more public/social housing commitments.
  \end{itemize}
\item The Left:
  \begin{itemize}
  \item (0) Source (Europarl link + speaker/date): use the HOUS report Europarl link above; The Left housing justice framing (Leila Chaibi, Irene Montero, Ilaria Salis, Martin Schirdewan).
  \item (1) Lexicon + framing:
  financialisation; speculation; rent caps; public housing; social right; commodification.
  ``Housing crisis comes from political choices that turned housing into a financial asset.''
  \item (2) Tools:
  rent controls/caps; large-scale public + cooperative housing investment; ban evictions without alternatives; restrict speculative ownership by investment funds; redirect spending to social housing.
  \item (3) EU role stance:
  pro-EU but critical of EU fiscal rules: housing crisis is linked to EU fiscal rules and state-aid constraints limiting public investment.
  \item (4) Procedure logic:
  opposed the final HOUS direction; rejected amendments that did not include stronger tenant protections/anti-speculation measures.
  \end{itemize}
\item ECR Group:
  \begin{itemize}
  \item (0) Source (Europarl link + speaker/date): use the HOUS report Europarl link above; ECR framing (national competence / subsidiarity).
  \item (1) Lexicon + framing:
  subsidiarity; national competence; private property; simplification; ``Europe of nations''.
  ``Over-regulation blocks national and market solutions.''
  \item (2) Tools:
  deregulation; planning simplification; tax reductions; decisions at national/local level; protect private property; combat ``illegal occupation'' framing.
  \item (3) EU role stance:
  skeptical: favours power at the lowest practicable level (individual/local/national instead of supranational bodies).
  \item (4) Procedure logic:
  supports the final direction on supply/simplification, but pushes back against binding EU rent regulation and cross-border housing standards (prefers national/local choices).
  \end{itemize}
\item PfE Group:
  \begin{itemize}
  \item (0) Source (Europarl link + speaker/date): use the HOUS report Europarl link above; PfE framing (national sovereignty/family housing).
  \item (1) Lexicon + framing:
  national sovereignty; family housing; energy prices; household burden.
  ``EU overreach + energy costs make homes unaffordable for ordinary families.''
  \item (2) Tools:
  national-level decisions; reduce energy costs; lower taxes for families; oppose EU housing mandates.
  \item (3) EU role stance:
  very skeptical: strong independent nations; decisions by nations, not imposed by EU structures.
  \item (4) Procedure logic:
  supports the final direction while pushing for limited EU competence; resists binding EU social-housing/tenant-protection mandates (prefers national control).
  \end{itemize}
\item ESN Group:
  \begin{itemize}
  \item (0) Source (Europarl link + speaker/date): use the HOUS report Europarl link above; ESN sovereignty/bureaucracy framing (ESN official channels).
  \item (1) Lexicon + framing:
  national sovereignty; people and regions; against bureaucracy; demographic change.
  ``EU waste of funds and wrong spending priorities.''
  \item (2) Tools:
  redirect EU budget toward national/regional needs; oppose EU regulation of housing markets; focus on demography.
  \item (3) EU role stance:
  very skeptical/hostile: ``EU budget must serve people and regions again, instead of getting lost in bureaucracy and prestige projects.''
  \item (4) Procedure logic:
  not fully specified: for the worksheet, write what you see in the debate flow (abstain/vote against parts) based on their sovereignty argument.
  \end{itemize}
\item Non-Inscrits:
  \begin{itemize}
  \item (0) Source (Europarl link + speaker/date): choose 1 specific Non-Inscrits MEP + paste their exact HOUS quote/speech and the PV minutes link.
  \item (1) Lexicon + framing:
  varies; no unified framing.
  \item (2) Tools:
  depends on the individual MEP.
  \item (3) EU role stance:
  varies from pro- to far-right depending on the individual.
  \item (4) Procedure logic:
  no unified position; base on the exact MEP statements you used.
  \end{itemize}
\end{itemize}

\section*{\color{eublue}Wrap-up (write this last)}
\begin{itemize}
\item \textbf{Similarities (3):}
  (1) Supply urgency: almost all groups treat the housing crisis as an emergency about availability (even if they disagree on the best fix).
  (2) Targeting vulnerable people: most groups connect housing to protecting vulnerable groups/tenants and affordability (including Housing First-style thinking).
  (3) Short-term rental regulation: multiple groups frame Airbnb/short-term rentals as a driver of local affordability problems (even if they disagree on how strict rules should be).
\item \textbf{Differences (3):}
  (1) Rent control: S\&D/Greens/The Left push rent-caps/controls, while EPP/Renew/ECR resist them ``because'' they frame rent control as harmful to investment/supply.
  (2) EU competence: S\&D/Greens/The Left want an EU strategy with funding/regulation ``because'' they see housing as a structural, cross-border failure; ECR/PfE/ESN push subsidiarity/national control ``because'' they frame housing as national sovereignty.
  (3) Green mandates: Greens (and often S\&D) push stricter energy/renovation requirements ``because'' they connect energy poverty with long-term habitability; PfE/ESN resist ``because'' they frame these rules as costly bureaucracy for families.
\item \textbf{One Vienna connection}: The Left + Greens match Vienna's non-market/prevention logic best; S\&D aligns with Vienna on the need for large-scale public/affordable investment; EPP/Renew/ECR clash with Vienna because they prioritize market-led supply/investment over keeping a large share of housing out of speculation.
\end{itemize}

\section*{Quick recall}
Revise: Unit 1 (four blocks), institutions. Full midterm guide in \texttt{week-6/midterm.tex}.

\section*{\color{eublue}Optional recap (from transcript) ... democratic deficit}
\begin{itemize}
\item Democratic deficit (plain words): the EU can make big decisions, but citizens don't always feel they can directly influence those decisions.
\item Early integration: decisions were shaped mostly by national politics and big institutions (especially the Council/Commission), while the EP initially had less direct impact on what citizens experienced.
\item EP at the start: because it wasn't directly elected and wasn't very visible, it could feel more like a discussion space than a real decision-maker.
\item Over time: reforms and treaty changes gradually increased the EP's legitimacy and influence (not all at once).
\item How debates get organized: political groups in the EP are built around left--right ideology across countries, so the link between what you vote for nationally and what you hear in EU debates can feel confusing.
\item 1979 turning point: the first direct elections boosted the EP's democratic mandate and awareness in public life.
\item Today: the EP shares legislative power and has budget influence, so it is more than symbolic; still, people can feel unsure about what their vote actually changes.
\item Citizen engagement (from the discussion): focus on clearer explanations of what each EU body does, and how to understand the EU political groups in real life.
\item Workshop connection: the groups that can push their language and proposals through the parliamentary process shape what legitimacy looks like to citizens.
\end{itemize}

\end{document}

