% Product Management – Midterm Cheat Sheet
% Compile with: pdflatex midterm-cheat-sheet.tex

\documentclass[9pt,landscape,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[left=1cm,right=2.8cm,top=1cm,bottom=1cm,marginparwidth=2.1cm,marginparsep=0.35em]{geometry}
\usepackage{multicol}
\usepackage{marginnote}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{soul}
\usepackage{fancyhdr}
\definecolor{lightpink}{RGB}{255,182,193}
\definecolor{lightpeach}{RGB}{255,218,185}
\definecolor{noteblue}{RGB}{173,216,230}
\newcommand{\handnote}[1]{\marginnote{\raggedright\small\color{noteblue}#1\vspace{0.6em}}}
\newcommand{\hlpink}[1]{\sethlcolor{lightpink}\hl{#1}\sethlcolor{lightpeach}}
\newcommand{\hlpeach}[1]{\sethlcolor{lightpeach}\hl{#1}}
\sethlcolor{lightpeach}
\setlength{\parskip}{0.3em}
\setlength{\columnsep}{0.8em}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[R]{\raisebox{0.8em}{\thepage}}
\fancypagestyle{plain}{\fancyhf{}\fancyfoot[R]{\raisebox{0.8em}{\thepage}}}
\raggedright

\begin{document}
\begin{center}
{\large\bfseries Product Management -- Midterm Cheat Sheet}\\[0.3em]
\small\textit{Define terms, give one example, tie to value creation/capture.}\\[0.6em]
\fbox{\parbox{0.92\textwidth}{\centering\small
\textcolor{black!80}{\textbf{Key:}} \colorbox{lightpink}{\strut\ \ \ } \textbf{Pink} = definitions \quad
\colorbox{lightpeach}{\strut\ \ \ } \textbf{Peach} = frameworks \& tips \quad
\colorbox{noteblue}{\strut\ \ \ } \textbf{Blue} = margin notes
\par}}
\end{center}
\vspace{-0.4em}

\begin{multicols}{2}

\section*{Unit 1 -- Value Creation vs.\ Capture}\handnote{Creation $\neq$ capture. Need both.}
\begin{itemize}[leftmargin=*,nosep]
\item \textbf{\hlpink{Value creation}} = Making something useful. Total value for users.
\item \textbf{\hlpink{Value capture}} = How much money you make. You need both.
\item \textbf{\hlpink{Market access}} = Distribution, channels. Teece: market access $\to$ value capture.
\item \textbf{Porter value chain}: Primary (production, delivery) + support (HR, tech). Value = resources + activities $\to$ users.
\item \textbf{Takeda case}: Spanish research 15K EUR $\to$ Takeda 250M EUR/year. Better market access, distribution, scale.\handnote{Classic example!}
\item \textbf{Value capture mechanisms}: Patents, branding, market access, co-specialized assets.
\item European challenge: smaller market reach limits value capture vs.\ global players.
\end{itemize}

\section*{Unit 2 -- BMC \& Product Design}\handnote{Validate before you build.}
\begin{itemize}[leftmargin=*,nosep]
\item \textbf{BMC}: Customer segments, value prop, channels, revenue, key resources, activities, costs.
\item \textbf{Product design}: Problem discovery $\to$ customer discovery $\to$ solution validation $\to$ build/launch.
\item \textbf{\hlpink{Lean validation}}: Don't spend until validated. Test. Learn. Iterate.
\item Problem--solution fit first. Go to market. Talk to customers. Don't assume.
\end{itemize}

\section*{Unit 3 -- Exploration vs.\ Exploitation}\handnote{Ambidextrous org.}
\begin{itemize}[leftmargin=*,nosep]
\item \textbf{\hlpink{Exploration}} (sensing) = Finding new opportunities. Searching.
\item \textbf{\hlpink{Exploitation}} (seizing) = Doing what works. Scaling. Capturing value.
\item Need both. Exploration finds; exploitation captures.
\item Microsoft: strong exploitation, weaker exploration.
\item \textbf{SDLC}: Plan $\to$ Build $\to$ Test $\to$ Deploy. Iterate.
\end{itemize}

\section*{Unit 4 -- Design Thinking}\handnote{Observe, don't ask.}
\begin{itemize}[leftmargin=*,nosep]
\item \hlpeach{Empathize $\to$ Define $\to$ Ideate $\to$ Prototype $\to$ Test}. Iterate.
\item Don't ask users what they want. Steve Jobs: ``People don't know what they want until you show them.''
\item \textbf{Observe behavior}. Ask about problems, past. Not solutions.
\item \textbf{\hlpink{Gemba}} = Go where work happens. Observe in real context.
\item \textbf{Two observers}: Reduces bias. Richer insight.
\item \textbf{\hlpink{Extreme users}}: Use product intensely. Reveal problems. IDEO cart: 22,000 kids/year injured.
\item Diverse teams (IDEO): engineers, psychologists, linguists. Different perspectives = better solutions.
\item Corporate trap: bosses reward desk time; best insight from the field.
\end{itemize}

\section*{Unit 5 -- Innovation \& Technology}\handnote{S-curve. Disrupt.}
\begin{itemize}[leftmargin=*,nosep]
\item \textbf{\hlpink{S-curve}}: Slow start $\to$ rapid growth $\to$ plateau $\to$ decline.
\item \textbf{\hlpink{Disruptive innovation}}: New tech starts lower, cheaper. Improves. Overtakes old.
\item \textbf{Innovator's dilemma}: Focus on current customers. Miss new thing. Old tech still profitable.
\item \textbf{Kodak}: Dominant in film. Failed digital. Canon, Sony, Nikon won.\handnote{Classic case.}
\item \textbf{iPhone}: Apple didn't invent; revolutionized. Touchscreen, size, ease.
\item \textbf{First mover}: Advantage or disadvantage if too early.
\item Radical innovation: often from outside established companies.
\item \textbf{Uber}: Created new market. Disrupted taxi.
\end{itemize}

\section*{Quick revision -- Can you explain\ldots?}\handnote{Run through before exam.}
\begin{itemize}[leftmargin=*,nosep]
\item Value creation vs.\ capture. Porter value chain. Teece \& market access.
\item Takeda case. BMC blocks. Product design process.
\item Exploration vs.\ exploitation. Design thinking 5 stages.
\item Why not ask users? Gemba, extreme users, two observers.
\item S-curve, disruptive innovation, innovator's dilemma.
\item Kodak, iPhone, Uber examples.
\end{itemize}

\section*{\hlpeach{Common question angles}}\handnote{Memorise these.}
\begin{itemize}[leftmargin=*,nosep]
\item \textbf{``Why create but not capture?''} Market access, distribution, patents, branding, scale. Takeda vs.\ Spanish research.
\item \textbf{``Apply design thinking.''} Empathize (observe) $\to$ define $\to$ ideate $\to$ prototype $\to$ test.
\item \textbf{``Exploration vs.\ exploitation?''} Both needed. Exploration finds; exploitation captures.
\item \textbf{``Why did Kodak fail?''} Innovator's dilemma; invested in film; didn't adapt; competitors did.
\end{itemize}

\end{multicols}

\newpage
\vspace*{0.3em}
\noindent\color{noteblue}
\setlength{\parskip}{0.4em}
\begin{multicols}{2}

\textbf{Unit 1 -- Value}\\
Creation $\neq$ capture. Need both. Market access.

\textbf{Unit 2 -- BMC \& Design}\\
Validate before build. Lean. Customer discovery.

\textbf{Unit 3 -- Exploration/Exploitation}\\
Sensing vs.\ seizing. Ambidextrous. SDLC.

\textbf{Unit 4 -- Design Thinking}\\
Observe don't ask. Gemba. Extreme users.

\textbf{Unit 5 -- Innovation}\\
S-curve. Disruptive. Kodak. Innovator's dilemma.

\textbf{Common angles}\\
Create vs capture. Design thinking. Kodak.

\end{multicols}
\vfill
\normalsize\normalfont\color{black}
\end{document}
